### 2022-03-01 paper/include/formatting.tex
add paper template

\section{Writing papers with \LaTeX}\label{cheiThu4}
This section provides a small introduction to writing papers with \LaTeX{}.
Uniquely label your sections\,/\,subsections, figures or equations.
You can afterwards reference labeled items.
Consider sections, figures and tables as proper names, i.\,e., capitalize them
when referencing, e.\,g.\ Section~\ref{cheiThu4}.
Equations such as
\begin{align}
	\nonumber G(f) &= \frac{1}{\sqrt{2\pi}}\int_{-\infty}^{\infty}
	g(t)e^{-j\omega ft} \operatorname dt\\
	&= \frac{1}{\sqrt{2\pi}}\int_{-\infty}^{\infty} g(t) \left (\cos(2\pi f t)
	-j\sin(2\pi ft) \right ) \operatorname dt
	\label{lai6Ohxo}
\end{align}
are labeled line by line and referenced by \eqref{lai6Ohxo}.
Equation~\eqref{lai6Ohxo} is typeset in an align environment, which allows to
align multiple lines at the same column.

\subsection{Units}
The \texttt{siunitx} package is your best friend when it comes to units.
It knows virtually any kind of unit such as \si{\kilo\meter}, \si{henry},
\si{\deci\bel}, and many more.
You can also use it to consistently typeset values, e.\,g.\ $\SI{1024}{\byte} =
\SI{1}{\kibi\byte} = \SI{1.024}{\kilo\byte}$.
You can even write something like $\SI{1000}{packets\per\second}$, and it can
be used in both text and math modes.

\subsection{Tables and figures}
Format your tables as shown in Table~\ref{shu1ioKo}.
\begin{table}
	\centering
	\caption{Example for a nice table}
	\label{shu1ioKo}
	\begin{tabular}{lllll}
		\toprule
		\textbf{SI prefix} & \textbf{Power of 10} && \textbf{Binary prefix} &
		\textbf{Power of 2}\\
		\midrule
		\si{\kilo} & $10^3$ && \si{\kibi} & $2^{10}$\\
		\si{\mega} & $10^6$ && \si{\mebi} & $2^{20}$\\
		\si{\giga} & $10^9$ && \si{\gibi} & $2^{30}$\\
		\si{\tera} & $10^{12}$ && \si{\tebi} & $2^{40}$\\
		\si{\peta} & $10^{15}$ && \si{\pebi} & $2^{50}$\\
		\bottomrule
	\end{tabular}
\end{table}
In contrast to figures, tables have their caption at the top.
Figure~\ref{Geivap7D} is placed inline by specifying the \texttt{h!} modifier
in the floating environment.
\begin{figure}[h!]
	\centering
	\begin{tikzpicture}[>=latex]
		\node[client,minimum size=10mm] (1) at (0,0) {};
		\node[server,minimum size=15mm] (2) at (4,0) {};
		\draw[->,line width=1pt, bend left] (1.north) to (2.north);
		\draw[->,line width=1pt, dashed] (2.west) to (1.east);
	\end{tikzpicture}
	\caption{A figure made with TikZ}
	\label{Geivap7D}
\end{figure}
Alternatively, you can tell \LaTeX\ to place floats at the top or bottom by
using the \texttt{t} and \texttt{b} modifiers, respectively.
You can also include graphic files such as PDF, PNG and JPEG by using
\texttt{\textbackslash{}includegraphics}.
However, make sure \textbf{not} to use images with an alpha channel.
Otherwise, the text of your paper will be rasterized when printed and will look
really bad.

\subsection{Citations}\label{UoQui0le}

You find a list of references at the end of the main file of your paper.
Add additional bibentries there as needed and cite them using the
\texttt{\textbackslash{}cite{}} macro.

Verbose citations must be enclosed by quotation marks with a citation
preceding or following the quoted text.
If you write a subsection in your own words but it is closely based on some
source, a citation at the beginning or end of that text block should suffice.

``%
Please number citations consecutively within brackets~\cite{b1}.
The sentence punctuation follows the bracket~\cite{b2}.
Refer simply to the reference number, as in~\cite{b3}---do not use
'Ref.~\cite{b3}' or 'reference~\cite{b3}' except at the beginning of a
sentence: 'Reference~\cite{b3} was the first $\ldots$'.'' \cite{b8}.

When you cite other papers for the first time, please list the author's names,
e.\,g.\ ``\ldots as shown by Jacobs and Bean in~\cite{b3}\ldots''.
In case there are more than two authors, you may also write ``\ldots as shown
by Eason et al.\ in~\cite{b1}\ldots'' instead.
Avoid a line break preceding the brackets by substituting the whitespace
between the preceding word and the \texttt{\textbackslash{}cite} macro by
``\textasciitilde{}''.

Invest a significant amount of time into finding the right related work:
\begin{itemize}
	\item Prefer scientific sources, i.\,e.\ papers, over websites.
	\item Do not blindly cite anything.
	Have a close look at the authors, the date of publications, and where the
	paper was published.
	In general, cite older literature first as it is likely to be closer to the
	original source of a topic.
	\item Do not hesitate to cite a paper multiple times, or find multiple
	independent sources for the same statement.
	However, cite the papers by date of publication.
	\item You will notice that many papers appear to be published multiple
	times by the same authors with some timely distance.
	Find and cite the oldest publication only.
	An exception may be papers that later appeared in journals as an extended
	version.
\end{itemize}

Citing URLs such as \cite{b9} is problematic for two reasons:
URLs tend to be long and cryptic and---more severe---are volatile, i.\,e.\,
they tend to break without warning.
Using services such as \url{archive.org} fix the latter problem but do not make
URLs more readable.
In any case, avoid URL shorteners since they represent another point of failure
and, in addition, hide the link target.
Consequently, avoid citing URLs whenever possible.
Some more citations~\cite{b4,b6,b7,b8,b9}.

\subsection{Some common mistakes}\label{eiceFe1u}
\begin{itemize}
	\item The word ``data'' is plural, not singular.
%	\item The subscript for the permeability of vacuum $\mu_{0}$, and other
%	common scientific constants, is zero with subscript formatting, not a
%	lowercase letter ``o''.
%	\item In American English, commas, semicolons, periods, question and
%	exclamation marks are located within quotation marks only when a complete
%	thought or name is cited, such as a title or full quotation.
%	When quotation marks are used, instead of a bold or italic typeface, to
%	highlight a word or phrase, punctuation should appear outside of the
%	quotation marks.
%	A parenthetical phrase or statement at the end of a sentence is punctuated
%	outside of the closing parenthesis (like this). (A parenthetical sentence
%	is punctuated within the parentheses.)
%	\item A graph within a graph is an ``inset'', not an ``insert''. The word
%	alternatively is preferred to the word ``alternately'' (unless you really
%	mean something that alternates).
	\item Do not use the word ``essentially'' to mean ``approximately'' or
	``effectively''.
%	\item In your paper title, if the words ``that uses'' can accurately
%	replace the word ``using'', capitalize the ``u''; if not, keep using
%	lower-cased.
%	\item Be aware of the different meanings of the homophones ``affect'' and
%	``effect'', ``complement'' and ``compliment'', ``discreet'' and
%	``discrete'', ``principal'' and ``principle''.
%	\item Do not confuse ``imply'' and ``infer''.
	\item The prefix ``non'' is not a word; it should be joined to the word it
	modifies, usually without a hyphen.
	\item There is no period after the ``et'' in the Latin abbreviation ``et
	al.''.
	\item The abbreviation ``i.\,e.'' means ``that is'', and the abbreviation
	``e.\,g.'' means ``for example''.
	\item The abbreviation ``i.\,e.'' is preceded and followed by commas while
	``e.\,g.'' is only preceded by a comma.
	\item Writing $f * g$ does \emph{not} indicate a multiplication but a
	convolution, and $f \times g$ indicates a cross product.
	Chances are, you mean and ordinary multiplication, which is simply written
	as $f \cdot g$.
	\item In English, the word ``that'' is never preceded by a comma.
	Writing something like ``The door that is blue \ldots'' uniquely identifies
	a specific door, while writing ``The door, which is blue \ldots'' merely
	describes one of many doors.
	Using the word ``which'' without a preceding comma in the previous example
	would be equivalent to using ``that''.
	\item Capitalize all words except for conjunctions like ``and'',
	``or'' etc.\ in your title and citations---even if others do not.
	\item Never use short forms such as ``don't''.
	Write ``do not'' instead.
	\item Between two headlines subordinate, e.\,g.
	\texttt{\textbackslash{}section} and \texttt{\textbackslash{}subsection},
	there must be some text.
	For instance, you might briefly outline the current section.
	\item Enumerations and lists consist of at least two items, not one.
	The same holds for subsections: do not use a subsection if there is only
	one.
	\item In English, you keep writing in lower case after a colon.
	\item The word ``eventually'' has nothing to do with the German word
	``eventuell''.
	\item Subordinate clauses starting with ``because'', ``since'', etc.\ are
	separated from the main clause by a comma only if the subordinate clause
	precedes the main clause.
	\item Figures, Tables, Sections etc.\ are considered proper names, i.\,e.\
	always write ``\ldots as shown in Section~\ref{UoQui0le}''.
	Make sure to capitalize the noun.
	An exception are equations.
	Here, the noun is completely omitted except when an equation is referenced
	at the beginning of a sentence.
	See \eqref{lai6Ohxo} at the beginning of Section~\ref{cheiThu4} for an
	example.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{How to find symbols in \LaTeX}
\emph{Detexify} \cite{b9} is an awesome website helping you with finding the
correct \LaTeX{} macro for hand-written symbols.

### 2022-03-01 paper/include/introduction.tex
add paper template

\section{Introduction}
This document shows you how to write your first paper in \LaTeX{}.
It provides you with some general information about \LaTeX{}, the fundamental
structure of most conference papers, and some common mistakes you should try to
avoid.

\subsection{Ease of Use}
Our seminar template ships with a sophisticated Makefile.
Simply type ``\texttt{make}'' and it will compile all \texttt{.tex} files in
the current working directory.
Additional targets may be specified in the \texttt{Makefile.conf.mk}, e.\,g.\
directories containing stand-alone figures.
In case you do not have an idea about that stuff, simply make sure not to put
any additional \texttt{.tex} files into the template's root directory.

\subsection{Maintaining the Integrity of the Specifications}
The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

### 2022-03-01 paper/include/structure.tex
add paper template

\section{Structure}
After copying the template to your git repository make sure you also
copied the (hidden) \texttt{.gitignore} file.
You also find additional directories which are explained in the following:

\begin{figure*}
		\centering
	\begin{subfigure}[c]{0.45\textwidth}
				\centering
		\includegraphics[width=.4\textwidth]{pics/example}
		\subcaption{An external figure.}
		\label{fig:external_pdf}	
	\end{subfigure}
	\begin{subfigure}[c]{0.45\textwidth}
		\includegraphics[width=\textwidth]{figures/example}
		\subcaption{An external figure which was built before included.}
		\label{fig:external_tex}
	\end{subfigure}
	\caption{This Figure has two subfigures and spans both columns.}
\end{figure*}

\begin{itemize}
	\item[\texttt{/pics}:] Here you can put all external figures which are
	not built for the paper. These are, for example, PNG or JPG files and
	vector graphics like PDF files. For an example have a look at
	Figure~\ref{fig:external_pdf}.

	\item[\texttt{/figures}:] If you do not want to build all your figures
	every time you compile your paper it is helpful to build them
	separately. All \texttt{.tex} and \texttt{.tikz} files within this directory
	are built automatically by the Makefile. Since these figures are built
	independently of the main document they have to be of type
	\texttt{standalone}. Make sure that you put no \texttt{.tex} or
	\texttt{.tikz} inside this directory which cannot be compiled
	independently.
	Figure~\ref{fig:external_tex} is an example for this. Notice that this
	PDF is only built if the figures source file has changed.

	\item[\texttt{/data}:] If you have larger amounts of data which you
	want to put into your paper, for example in form of a table or a plot
	you can import the data directly from another file.
	Figure~\ref{fig:external_tex} reads the red sample points from a CSV
	file located in this directory.
\end{itemize}

### 2022-03-01 paper/paper.tex
add paper template

% Do not change the section below
% ============================================================================
\documentclass[conference,compsoc,a4paper]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{nimbusmononarrow}
\usepackage[T1]{fontenc}

\usepackage{balance}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{url}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\newcommand{\fixme}[1]{\textcolor{red}{[FIXME: #1]}}
% ============================================================================

% Add additionale LaTeX packages if needed here
% ============================================================================
\usepackage[%
	detect-all,
	binary-units=true,
]{siunitx}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{moeptikz}
% ============================================================================

\begin{document}

% Add paper title here, most likely you want to delete the \thanks{} macro
% ============================================================================
\title{Paper Title}
% ============================================================================

% Update author information
% ============================================================================
\author{%
	\IEEEauthorblockN{%
		Your Name,
		Advisor's Name\IEEEauthorrefmark{1}
	}
	\IEEEauthorblockA{%
		\IEEEauthorrefmark{1}Chair of Network Architectures and Services,
		Department of Informatics\\
		Technical University of Munich, Germany\\
		Email: your@mail.address, advisor@net.in.tum.de
	}
}
% ============================================================================

\maketitle

% Edit include/abstract.tex to write your paper's abstract
% ============================================================================
\begin{abstract}
\input{include/abstract}
\end{abstract}
% ============================================================================

% List keywords of your paper in lower-case below
% ============================================================================
\begin{IEEEkeywords}
software-defined networks, measurement, hight-speed networks
\end{IEEEkeywords}
% ============================================================================

% For each section of your chapter add one source file in the include folder
% ============================================================================
\input{include/introduction}
\input{include/related_work}
\input{include/formatting}
\input{include/structure}
\input{include/conclusion}
% ============================================================================

% Put your references in the paper.bib file
% ============================================================================
\balance

\bibliographystyle{IEEEtran}
\bibliography{paper}
% ============================================================================

\end{document}

### 2022-11-04 paper/include/structure.tex
remove necessity for make

@@
 	\end{subfigure}
-	\begin{subfigure}[c]{0.45\textwidth}
-		\includegraphics[width=\textwidth]{figures/example}
-		\subcaption{An external figure which was built before included.}
-		\label{fig:external_tex}
-	\end{subfigure}
-	\caption{This Figure has two subfigures and spans both columns.}
 \end{figure*}
@@
 
-	\item[\texttt{/figures}:] If you do not want to build all your figures
-	every time you compile your paper it is helpful to build them
-	separately. All \texttt{.tex} and \texttt{.tikz} files within this directory
-	are built automatically by the Makefile. Since these figures are built
-	independently of the main document they have to be of type
-	\texttt{standalone}. Make sure that you put no \texttt{.tex} or
-	\texttt{.tikz} inside this directory which cannot be compiled
-	independently.
-	Figure~\ref{fig:external_tex} is an example for this. Notice that this
-	PDF is only built if the figures source file has changed.
-
 	\item[\texttt{/data}:] If you have larger amounts of data which you
@@
 	you can import the data directly from another file.
-	Figure~\ref{fig:external_tex} reads the red sample points from a CSV
-	file located in this directory.
 \end{itemize}

### 2022-11-04 talk/include/slides.tex
remove necessity for make

\usepackage[utf8]{inputenc}
\usepackage{tumcd/packages}
\usepackage{tumcd/beamermods}

% For beamer mode (default):
\author[S. G\"unther]{Stephan Günther}
\title[Networking]{Something with Networking}

% Uncomment to add advisors for presentation in Oberseminar
%\advisor{Herrmann B. Wolfgang}

% Uncomment to add type for presentation in Oberseminar
% Usage: \thesistype{intermediate | final}{bachelor | master | idp | gr}
%\thesistype{intermediate}{gr}

% Uncomment to configure date in dd-mm-yyyy format
%\newdate{date}{25}{05}{2017}
%\date{\displaydate{date}}

% Uncomment to add a venue to the title slide
%\venue{International Conference on Conferencing 2018 \\ Garching b. München, Germany}

% For lecture mode (use package option 'lecture'):
%\lecture[GRNVS]{Grundlagen Rechnernetze und Verteilte Systeme}
%\module{IN0010}
%\semester{SoSe\,2016}
%\assistants{Johannes Naab, Stephan Günther, Maurice Leclaire}

\usepackage{pgfpages}
\usepackage{ifthen}
% ============================================================================
% jobname solution
% ============================================================================
\newif\ifsolution%
\ifthenelse{\equal{\detokenize{notes}}{\jobname}}{%
\setbeameroption{show notes on second screen=bottom}
\setbeamercolor{note page}{bg=white, fg=black}
\setbeamercolor{note title}{bg=white!95!black, fg=black}
}{
}

% TeXLive 2018 compatibility: https://tex.stackexchange.com/questions/426088/texlive-pretest-2018-beamer-and-subfig-collide
\makeatletter
\let\@@magyar@captionfix\relax
\makeatother

### 2024-11-20 paper/figures/fallback.tex
Initial submit.

 \begin{tikzpicture}[
    scale=0.4, % Further reduced scale
    node distance=2cm, % Further reduced distance
    % user/.style={circle,draw,minimum size=0.6cm},
    % attacker/.style={rectangle,draw,fill=red!20,minimum width=1cm,minimum height=0.7cm},
    % server/.style={rectangle,draw,minimum width=1cm,minimum height=0.7cm}
    censor/.style={rectangle,draw,fill=red!20,minimum width=1cm,minimum height=0.7cm},
    proxy/.style={rectangle,draw,minimum width=1cm,minimum height=0.7cm},
    client/.style={rectangle,draw,minimum width=1cm,minimum height=0.7cm},
    destination/.style={rectangle,draw,minimum width=1cm,minimum height=0.7cm},
    webserver/.style={rectangle,draw,minimum width=1cm,minimum height=0.7cm}
]
    % Define nodes with shorter labels
    % \node[user] (alice) {A};
    % \node[attacker] (mitm) [right of=alice] {M};
    % \node[server] (server) [right of=mitm] {S};
    \node[client] (client) {C};
    \node[censor] (censor) [below of=client] {P};
    \node[proxy] (proxy) [right of=client] {S};
    \node[destination] (destination) [right of=proxy] {D};
    \node[webserver] (webserver) [below of=destination] {F};

    % Shorter arrows and smaller labels
    % \draw[->,thick] (alice) to[bend left=20] node[above,font=\tiny] {Msg} (mitm);
    % \draw[->,thick] (mitm) to[bend left=20] node[above,font=\tiny] {Mod} (server);
    % \draw[->,thick] (server) to[bend left=20] node[below,font=\tiny] {Rsp} (mitm);
    % \draw[->,thick] (mitm) to[bend left=20] node[below,font=\tiny] {Mod} (alice);
    \draw[->] (client) to node[above, font=\tiny] {Req} (proxy);
    \draw[dashed] (censor) to[bend left=20] node[above, font=\tiny] {Prb} (proxy);
    \draw[->] (proxy) to node[above, font=\tiny] {FWD} (destination);
    \draw[dashed] (proxy) to[bend left=20] node[above, font=\tiny] {FB} (webserver);
\end{tikzpicture}

### 2024-11-20 paper/figures/mitm.tex
Initial submit.

\begin{tikzpicture}[
    scale=0.4, % Further reduced scale
    node distance=2cm, % Further reduced distance
    user/.style={circle,draw,minimum size=0.6cm},
    attacker/.style={rectangle,draw,fill=red!20,minimum width=1cm,minimum height=0.7cm},
    server/.style={rectangle,draw,minimum width=1cm,minimum height=0.7cm}
]
    % Define nodes with shorter labels
    \node[user] (alice) {A};
    \node[attacker] (mitm) [right of=alice] {M};
    \node[server] (server) [right of=mitm] {S};

    % Shorter arrows and smaller labels
    \draw[->,thick] (alice) to[bend left=20] node[above,font=\tiny] {Msg} (mitm);
    \draw[->,thick] (mitm) to[bend left=20] node[above,font=\tiny] {Mod} (server);
    \draw[->,thick] (server) to[bend left=20] node[below,font=\tiny] {Rsp} (mitm);
    \draw[->,thick] (mitm) to[bend left=20] node[below,font=\tiny] {Mod} (alice);
\end{tikzpicture}

### 2024-11-20 paper/figures/proxy.tex
Initial submit.

\begin{tikzpicture}[
    scale=0.4,
    node distance=2cm,
    user/.style={circle,draw,minimum size=0.6cm},
    proxy/.style={rectangle,draw,fill=green!20,minimum width=1cm,minimum height=0.7cm},
    server/.style={rectangle,draw,minimum width=1cm,minimum height=0.7cm},
    firewall/.style={rectangle,draw,fill=red!20,minimum width=1cm,minimum height=0.7cm}
]
    % Define nodes
    \node[user] (user) {U};
    \node[firewall] (fw) [right of=user] {FW};
    \node[proxy] (proxy) [right of=fw] {P};
    \node[server] (server) [right of=proxy] {S};

    % Draw arrows and connections
    \draw[->,thick] (user) to[bend left=20] node[above,font=\tiny] {Enc} (proxy);
    \draw[dashed] (user) -- (fw);
    \draw[dashed] (fw) -- (proxy);
    \draw[->,thick] (proxy) to[bend left=20] node[above,font=\tiny] {Req} (server);
    \draw[->,thick] (server) to[bend left=20] node[below,font=\tiny] {Rsp} (proxy);
    \draw[->,thick] (proxy) to[bend left=20] node[below,font=\tiny] {Enc} (user);
\end{tikzpicture}

### 2024-11-20 paper/paper.tex
remove necessity for make
Initial submit.

@@
-% Do not change the section below
-% ============================================================================
-\documentclass[conference,compsoc,a4paper]{IEEEtran}
+\documentclass[conference]{IEEEtran}
 \IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+%Template version as of 6/27/2024
 
-\usepackage{nimbusmononarrow}
-\usepackage[T1]{fontenc}
-
-\usepackage{balance}
-\usepackage{cite}
+% \usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{graphicx}
+% Graphic path
+% \graphicspath{{./pics/}}
 \usepackage{textcomp}
 \usepackage{xcolor}
-\usepackage{subcaption}
-\usepackage{url}
+\usepackage{orcidlink}
+\usepackage{hyperref}
+\usepackage{multirow}
+\usepackage{float}
+\usepackage{tikz}
+\usetikzlibrary{positioning}
 
@@
 
-\newcommand{\fixme}[1]{\textcolor{red}{[FIXME: #1]}}
-% ============================================================================
-
-% Add additionale LaTeX packages if needed here
-% ============================================================================
-\usepackage[%
-	detect-all,
-	binary-units=true,
-]{siunitx}
-\usepackage{booktabs}
-\usepackage{tikz}
-\usepackage{moeptikz}
-% ============================================================================
-
+% \usepackage[
+% backend=biber,
+% style=IEEEtran,
+% sorting=ynt
+% ]{biblatex}
+% \addbibresource{ref.bib}
 \begin{document}
 
-% Add paper title here, most likely you want to delete the \thanks{} macro
-% ============================================================================
-\title{Paper Title}
-% ============================================================================
+\title{The Eternal Adversary between Censor and Circumvention}
+\footnotesize
+% \textsuperscript{*}Note: Sub-titles are not captured for https://ieeexplore.ieee.org  and should not be used
+%\thanks{Identify applicable funding agency here. If none, %delete this.}
 
-% Update author information
-% ============================================================================
-\author{%
-	\IEEEauthorblockN{%
-		Your Name,
-		Advisor's Name\IEEEauthorrefmark{1}
-	}
-	\IEEEauthorblockA{%
-		\IEEEauthorrefmark{1}Chair of Network Architectures and Services,
-		Department of Informatics\\
-		Technical University of Munich, Germany\\
-		Email: your@mail.address, advisor@net.in.tum.de
-	}
-}
-% ============================================================================
-
+\author{\IEEEauthorblockN{1\textsuperscript{st} Guanru Chen}
+\IEEEauthorblockA{\textit{Technische Universität München} \\
+\textit{guanru.chen@tum.de \orcidlink{0009-0004-0715-910X}}}}
 \maketitle
 
-% Edit include/abstract.tex to write your paper's abstract
-% ============================================================================
 \begin{abstract}
-\input{include/abstract}
+This paper review and discussion the adversary between censorship and approaches to circumvent those restrictions from technical perspective
 \end{abstract}
-% ============================================================================
 
-% List keywords of your paper in lower-case below
-% ============================================================================
 \begin{IEEEkeywords}
-software-defined networks, measurement, hight-speed networks
+Censorship, Firewall, Proxy, Encryption, TLS
 \end{IEEEkeywords}
-% ============================================================================
 
-% For each section of your chapter add one source file in the include folder
-% ============================================================================
-\input{include/introduction}
-\input{include/related_work}
-\input{include/formatting}
-\input{include/structure}
-\input{include/conclusion}
-% ============================================================================
+\section{Introduction}
+Restrictions of network connectivity are everywhere and are deployed for versatile reasons: companies use such technologies for security audits and the prevention of commercial secrets leakages, parents use them to control children's screen time, and regimes also deploy them on a large scale to stifle freedom of thought… Then there come some approaches that try to circumvent it, and we are going to discuss the adversity between the rivals by focusing on technologies and their evolution from a technical perspective.
+The primary idea of restriction is simple: as an Internet service provider (ISP), censors can drop a package with specific criteria (such as destination IP, destination Port, protocol in IP 5 tuple).
+The primary idea of a proxy is also simple: through an external server as a relay (or springboard) to reach the site blocked by the local network.
 
-% Put your references in the paper.bib file
-% ============================================================================
-\balance
+\section{Methodology}
+We analyze typical protocols statically in our cloud servers and visualize the data.
 
-\bibliographystyle{IEEEtran}
-\bibliography{paper}
-% ============================================================================
+\subsection{Protocols that We Took Into Consideration}\label{AA}
+We chose typical protocols with different ideas:
+\begin{enumerate}
+    \item \href{https://shadowsocks.org}{Shadowsocks} (to be more specific, we use its newest rust-based implementation since it is still under active maintenance) and \href{https://gitlab.com/yawning/obfs4}{obfs4 bridge}, which represents the idea of encrypting and obfuscating.
+    \item \href{https://trojan-gfw.github.io/trojan/}{trojan-gfw} and \href{https://github.com/klzgrad/naiveproxy}{naiveproxy}, which are practices of the concept, to camouflage HTTPS connection and to utilize TLS for security.
+    \item Plain HTTPS connection as a control group.
+\end{enumerate}
+
+\subsection{Set Up Proxy Server}
+We configured the remote proxy server and the corresponding dependencies since most server sides of the TLS-based protocols require an upstream Web Server to forward unauthorized web traffic (which is always considered an active probe).
+We also need to obtain a SSL certificate issued by a qualified CA for security.
+We published the notes and more technical details about the servers' configuration processes in the seminar repository. We will also elaborate it in the presentation.
+
+\subsection{Processing and Analysis }
+We implemented a simple Python script with \href{https://dpkt.readthedocs.io/en/latest/}{an external Library, dpkt}, which spares the time and work to decode recorded Pcap files and strip neglectable packet headers of corresponding lower OSI levels (we should focus on proxy traffic).
+In the analysis phase, we select two aspects (the most remarkable characteristics of encrypted protocols): entropy and packet length.
+Additionally, we should consider and measure their variations in the temporal domain.
+For TLS-based protocols, their TLS fingerprints introduce a new characteristic.
+The concept of TLS fingerprint is a combination of various factors according to the standard of SSL/TLS, key exchange algorithm, asymmetric encryption algorithm, symmetric encryption algorithm, MAC algorithm, SSL version, and further derived experimental features, e.g.
+Session Resumption, multiplex/HTTP2).
+Sorting and evaluating such versatile, statistically relevant data requires further consideration.
+However, we still implement some auxiliary functions to retrieve cipher suite information from Client Hello (if no encryption is applied).
+We have made the code available in the seminar repository.
+
+\section{The Censor}
+Almost all firewalls try to restrict only specific traffic, with interference in authorized connections as little as possible, so there is a need for mechanisms to distinguish between valid and invalid connection attempts.
+
+\subsection{The Detection}
+Generally speaking, two kinds of approaches try to achieve this goal: passive tests, which try to analyze the existing data and figure out characteristics and patterns that make a disguised traffic identifiable, and active probes, which use measurements such as replay attack, tampering data and Man-in-the-middle attack.
+We will discuss different approaches that try to distinguish "unauthorized" traffic.
+
+\subsection{The Passive Detection}
+Passive detection means that the censor analyzes the traffic that goes through their infrastructures (the "Infrastructures" are often gateways but should not be limited to gateways, for example, they can also use optical splitters to intercept traffic from fibers).
+When people use network tools such as Wireshark, tcpdump, or CharlesProxy to check traffic , they do almost the same work with the censor, but beyond the idea, the tools that are adopted by censors can sometimes be much more sophisticated.
+Traffic can be inspected in multiple OSI Layers.
+Also, different Protocols can be analyzed with different measurements depending on their characteristics (for example, we can analyze a HTTPS traffic with the help of A Man in the Middle (MITM) Attack).
+
+\subsubsection{Effort in Decryption}
+ The most straightforward way to decide whether a connection is valid is to retrieve the carried payload and censor it.
+But in the age of AEAD and HTTPS/SSL, it will always become complicated (or can only be partially implemented in a very stringent condition like an attack which utilizes a classical vulnerability Heartbleed \cite{Heartbleed} (In most scenarios, it has been patched).
+ \begin{itemize}
+    \item  For symmetric-key algorithms, some extremely old encryptions before The Advanced Encryption Standard(AES), such as single DES and RC-4 can be solved in a reasonable time.
+But generally speaking, that is not a feasible approach.
+Nowadays, most protocols (both TLS and non-TLS based) have widely adopted AES algorithms.
+    \item - There can be more chances when we consider the asymmetric-key exchange phases, which only happen when a TLS-based protocol tries to establish.
+For example, MITM Attack, but I will elaborate in the following module, which goes on “Active Probing” since it needs to intercept and tamper packets.
+Shor’s Algorithm \cite{Shors_Algorithm} also provides a possibility to solve the question in polynomial time.
+Still, due to versatile technical limitations, it’s generally not practical (such an existing quantum computer’s capability is like "it could tell you there is 70\% chance 15 = $3\times$5").
+ \end{itemize}
+
+\subsubsection{Entropy}
+Entropy is a remarkable factor in detecting a protocol, but it could not be the single factor since almost all ciphertexts have a high entropy.
+But it can be a factor together with the amount of traffic to make a preliminary decision whether a connection is suspicious and needs further investigation: high entropy(encrypted), long-lasting but non-HTTPS traffic can be an unauthorized attempt to connect, communicate, and transfer data between proxy client and proxy server (But the combination of those factors is not sufficient to determine it brutally, or it will introduce errors far beyond an acceptable range.)
+We collected some of the typical encrypted protocols' traffic (both proxy protocols and genuine HTTPS protocol) and calculated its general entropy.
+Here is the overall entropy of each proxy protocol
+% we also verified our result with ent \cite{ent}.
+
+\begin{table}[h]
+\centering
+\caption{Average Entropy for Common Protocols}
+\resizebox{\columnwidth}{!}{
+\begin{tabular}{|l|lllll|}
+\hline
+\multirow{2}{*}{} & \multicolumn{5}{c|}{Protocol Name}                                                                                                   \\ \cline{2-6}
+                  & \multicolumn{1}{l|}{Shadosocks} & \multicolumn{1}{l|}{HTTPS} & \multicolumn{1}{l|}{NaiveProxy} & \multicolumn{1}{l|}{Trojan} & Obfs4 \\ \hline
+Entropy          & \multicolumn{1}{l|}{7.999}      & \multicolumn{1}{l|}{7.977} & \multicolumn{1}{l|}{7.992}      & \multicolumn{1}{l|}{7.858}  & 7.999 \\ \hline
+\end{tabular}%
+}
+\end{table}
+
+\subsubsection{TLS Fingerprinting}
+For a TLS-based protocol, it additionally exposes “Fingerprints”, which is mainly about offered and chosen cipher suits(key exchange, MAC, Key Length…).
+There have been many protocols that try to camouflage HTTPS connections by design.
+The HTTPS (to be more specific, TLS, Transport Layer Security on which HTTPS is built ) protocol stack brings extra advantage in the prospect of security since it is designed and verified rigorously in terms of cryptography, for example, with TLS's implementation, developers can be exempt from worrying protecting the server from Reply Attack (without Security features provided by TLS, they must build a Bloom Filter on their own.
+But a Bloom Filter can also be a suspicious characteristic)
+On the other hand, a failed try to camouflage HTTPS traffic can be one of the most "deadly" fatal remarkable characteristics \cite{TLS_Fingerprinting}.
+Except for the ciphers, there are many more factors that can be measured as "Fingerprints" of HTTPS connections, which are initialized by a client, such as SSL/TLS version, Certificates, multiplex (for HTTP/2), and more experimental features such as early data, TCP Fast Open (TFO).
+Such "Fingerprints" can be used in conjunction with other factors, such as the packet length.
+we will elaborate on it later in the section "Circumvention and Mitigation".
+There was a widely used Shadowsocks’ fork, ShadowsocksR, which tried to imitate HTTPS with an artificial SSL handshake, but when confronting a relatively mature and well-designed censor technology, those camouflages turned out to be a fatal vulnerability: it did not establish a real SSL connection, just attempt to make fake handshake and attach a artificial HTTPS header.
+
+\subsubsection{Behavior}
+Behavior is a generic factor that covers the reaction of both client and server in different scenarios: how do they communicate?
+Do they send heartbeat packets to keep living?
+How do they handshake?
+How do they exchange control instruction?
+These factors allow almost all professional routers to filter connections with OpenVPN or Wireguard Protocol.
+But we will not focus on proxies such as obfs4 and Shadowsocks because most of the VPNs, together with SSH Tunnels, are not designed to have abilities to bypass censors (We are not going to talk about and consider some modified versions of OpenVPN, which are advertised as capable for censor bypassing, because they are always proprietary and do not follow an open standard).
+There are also behaviors worth researching and discussing, such as how servers react to active probes.
+We will talk about it later.
+
+\subsubsection{Packet Length}
+The length of packets that carry the payload and header or instructions of the proxy protocol is also a significant feature of protocols.
+An example is Trojan-gfw, which utilizes the TLS protocol stack but does not resize its packets, which leads to some packets with outstanding extreme lengths.
+The following figures that we depicted show the occurrences of length respectively for each protocol.
+There are also length statistics of standard HTTPS traffic, which can be the control group.
+Naiveproxy uses padding and packet resizing to mitigate recognizing and categorization in the aspect of packet length.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.45\textwidth]{pics/occurrence_of_length_trojan.png}
+    \caption{The Length-Occurrence Statistics of Trojan-gfw}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{pics/occurrence_of_length_https.png}
+    \caption{The Length-Occurrence Statistics of HTTPS}
+    % \centering
+    % \includegraphics[width=0.45\textwidth]{occurrence_of_length_obfs4.png}
+    % \caption{The Length-Occurrence Statistics of obfs4}
+    % \centering
+    % \includegraphics[width=0.45\textwidth]{occurrence_of_length_shadowsocks.png}
+    % \caption{The Length-Occurrence Statistics of Shadowsocks}
+    \centering
+    \includegraphics[width=0.45\textwidth]{pics/occurrence_of_length_naiveproxy.png}
+    \caption{The Length-Occurrence Statistics of Naiveproxy}
+\end{figure}
+
+\subsubsection{Temporal Domain (Timing Analysis)}
+As a connection is a dynamic process, how traffic varies in the temporal domain is worth researching.
+The timing analysis  shows its significance, especially when a remarkable process happens, such as a handshake.
+We depicted The variations of different protocols in the temporal domain.
+It is worth noticing that because of Shadowsocks' nature (they use preset symmetric private key), it does not need key exchange and handshake (the connection itself can be stateless)
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.45\textwidth]{pics/temporal_statistic_of_entropy_shadowsocks.png}
+    \caption{The Entropy Statistics of Shadowsocks in Temporal Domain}
+\end{figure}
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.45\textwidth]{temporal_statistic_of_entropy_https.png}
+%     \caption{The Entropy Statistics of HTTPS in Temporal Domain}
+%     \includegraphics[width=0.45\textwidth]{temporal_statistic_of_entropy_naiveproxy.png}
+%     \caption{The Entropy Statistics of Naiveproxy in Temporal Domain}
+%     \centering
+%     \includegraphics[width=0.45\textwidth]{temporal_statistic_of_entropy_trojan.png}
+%     \caption{The Entropy Statistics of Trojan-gfw in Temporal Domain}
+% \end{figure}
+
+\subsubsection{Other Miscellaneous Factors}
+There are also some miscellaneous outstanding characteristics, such as the structure of packets, special headers or bits (which is in even plaintext when a handshake happens).
+Classical VPNs and standard proxies that are not designed with the intention of providing censor bypass capability always have these characteristics.
+That's the reason most of industrial routers/gateways can distinguish and mark traffic as OpenVPN or Wireguard.
+
+\subsection{The Active Detecion}
+Active detection can be used as a supplement, but it is not so widely adopted as passive inspection (But in authoritarian countries that have an extreme network censor it is adopted), the main reason is scanning, probing, and sniffing are always regarded as "sensible" activities and associated with suspicious Hack activities.
+But for national-level censors, they can control a large scale of malicious Bot Net.
+Because they have not only resources (of course, money from taxpayers) but also control the infrastructures of the backbone network.
+
+\subsubsection{Man in the Middle Attack}
+MITM attack is a common and practical way to decrypt TLS traffic due to the nature of asymmetric encryption:
+it is normal to practice MITM attacks in conjunction with downgrading attacks since network suppliers(for example ISPs, network administrators of enterprises or government) can always intercept, tamper, and mirror traffic which is carried by their links.
+Such attack utilizes the nature of asymmetrical encryption and key exchange process, which happends when a SSL/TLS secure channel try to establish: The asymmetric encryption can guarantee the connection between peers is secure, but it cannot verify who is the peer.
+That means without further extra verification of the peer's identity (like a Certificate issued by Certificate Authority CA), a Man in the Middle can easily fake the genuine peer and decrypt all the messages in your communication, as the following figure shows: Through asymmetric encryption, there are two "secure" channels built, but asymmetric encryption itself can not guarantee who the peer in another side of the "secure" channel is.
+
+\begin{figure}[!h]
+\centering
+\input{figures/mitm}
+\caption{MITM attack: Attacker (M) intercepts messages between sender (A) and server (S).}
+\label{fig:mitm}
+% \vspace{-0.2cm}
+\end{figure}
+
+Furthermore, they can even attack at the level of certification suites, such as coercing all the devices that are allowed to access their local network install and trust their own root certificate.
+There are still means to solve that problem effectively: embed own certificate suites in apps (many applications, especially in the Android system, have adopted such “certificates pinning” mechanism.)
+
+\subsubsection{Replay Attack Targets to Non-TLS Server}
+Protocols that do not use Authenticated Encryption with Associated Data (AEAD) algorithm are especially vulnerable when confronting replay attacks.
+Without a reliable mechanism to calculate an associated Message Authentication Code(MAC), authority and integrity cannot be guaranteed, though the payload will still not leak.
+The control of the gateway gives ISPs (or other censors) the capabilities to block, intercept, surveillance, and tamper with any packet, as long as the packet is carried by their data link.
+So they can send probes, evaluate, and analyze how servers react to it: if servers’ reactions are specious, which means they have regular, identifiable “abnormal” behavior, for example, a server has different behavior when handling altered and not altered replay probe, because such behavior is stably distinguishable with other normal network services.
+Things can be even worse when the server can not filter those reply attacks and treats it like a valid request and gives back a response (because of the encryption, an attacker cannot really retrieve any content, but it is sufficient to identify and block the proxy server)\cite{Active_Probing}.
+The worst case happens because of both the detailed implementation defect and the nature of “stream Cipher” (non-AEAD implementations).
+In the period around October 1.
+2018, a "sensitive" period, when Chinese Communist Party regime celebrated their illegal seizure of power, they reinforced the firewall and probably for the first time put this new active probe technique into practice and that is indeed effective since Shadowsocks(R) with stream cipher at that time is one of the most popular protocols and almost all the user report they are affected.
+After that, these new techniques and their underlying mechanisms were for the first time recognized and uncovered by developers.
+There is some Mitigation of that: initially, stream ciphers(which means ciphers except AES-GCM and chacha20-poly1305 family) should be deprecated.
+As a mitigation, Bloom Filter is also adopted in those proxies (but the existence of Bloom Filter in the server side may even be a new feature).
+
+\subsubsection{Replay Attack Targets to TLS Server}
+It is rational, to browse the Internet with HTTPS protocol, though that is both highly encrypted and long-lasting.
+But active probing still has usages: its idea is not so cryptographic, yet more logical: check the server, it is suspicious when there is no real content to offer like a real web server(or something like WebDAV or git server, which also offers web access).
+We will have further discussions later in the "Circumvention and Mitigation" section.
+% The approach to mitigating those kinds of probes is also straightforward, such as setting up a real web server that can offer dynamic or static web content(such as Nginx, or Apache).
+When the proxy server receives a probing, in other words, when it receives a HTTPS connection but cannot validate the payload, it forwards it to the web server and returns regular web content (developers call it "fallback").
+
+\subsection{Restriction}
+After traffic is identified, a censor can take measures to block or restrict it.
+It is about two questions:
+\begin{enumerate}
+    \item \textbf{How can a censor select the designated traffic as precisely as possible?}
+    \item \textbf{How can a censor impose a restriction on the designated traffic as precisely as possible?}
+\end{enumerate}
+There are versatile factors that can be the basis of restriction.
+The concrete approaches to the imposition of restrictions are also different.
+Generally speaking, all those techniques are highly associated with and based on the nature of the OSI 7 Level Model.
+
+\subsubsection{TCP/IP 5 Tuple}
+The primal idea of this problem is straightforward: use TCP/IP 5 tuple to specify a connection, as a system administrator does when they write an iptables statement.
+It is a Layer 3 (the Network Layer) and Layer 4 (the Transport Layer) based approach.
+
+\subsubsection{Block by SNI}
+Block a connection by SNI utilizes the nature of the HTTPS protocol stack, which lies on Layer 7 (the Application Layer).
+During the HTTPS handshake, a SNI delivers additional information to servers.
+This plaintext message cannot only be a factor in restrictions but also a defect in privacy since it is in plaintext and leaks the name of the name website to which a client wants to connect.
+So censors can block a HTTPS connection when the SNI is matched.
+It can also be mitigated with some experimental features such as ESNI and ECH, we will also discuss it later in the section "Circumvention and Mitigation".
+
+\subsubsection{Block by Dropping Packet}
+It is the most basic but feasible approach to restrict network access in a local network, and it will make a remote site at specific IP addresses unreachable.
+But it can be incapable in some scenarios, such as in authoritarian, even totalitarian states such as China or Iran, both all the ISPs that provide local network access and the physical channels (such as international submarine communication cables and fibers) are under control, that means if regimes decide to adopt a allow list (e.g., only allow users in local network access local websites), all the protocols will be in vain because there is no side channel (Sometimes problems can be more than technical issues).
+
+\subsubsection{Reset TCP Connection}
+This approach is based on the behavior of the Layer 4 (the Transport Layer) TCP protocol stack: when a RST packet is received, the socket should stop the connection and exit.
+Stateless connection protocols like raw UDP or QUIC are not affected.
+But generally speaking, those stateless protocols are not a practical mitigation, because they are not widely used compared with TCP-based protocols, which means those family of protocols are not a good target to imitate and camouflage.
+There are further problems, which we will discuss later.
+
+\subsubsection{DNS Pollution}
+That is also a well-known, widely and early adopted approach.
+Its basic mechanism is also straightforward: the original DNS server is unencrypted and will not be validated.
+The DNS system also has a decentralized nature that makes such pollution feasible: The downstream malicious DNS servers answer a query before the authentic Answer.
+Due to this known defect (and privacy weakness), DoH (DNS over HTTPS), DNSSec, and DoT (DNS over TLS)  are proposed as feasible mitigation.
+To this day, especially DoH is adopted, and also because of the decentralized essence, an anycast DNS server service (such as 1.1.1.1) cannot easily be blocked, but a censor can still disturb the query directly towards an authentic DNS Service located in the outside of the local network.
+
+\subsubsection{Quality of Service (QoS)}
+Stateless-protocol-based communications (it does not need to establish a "connection") such as UDP and Quic cannot be reset like TCP connections, but the censor (carrier) can also aggravate the quality of such "connection" by irregularly dropping packets, intentionally increasing the delay, make the transmission time become almost unacceptable.
+For stateful, connection-based protocols such as TCP connection, such interference can be more fatal.
+
+\section{Circumvention and Mitigation}
+Generally speaking, proxies and VPNs are based on the idea of "Side Channel", which provides an unrestricted side channel that gives access to sites and addresses whose access is restricted in the local network.
+
+\begin{figure}[!h]
+\centering
+\input{figures/proxy}
+\caption{Proxy-based network bypass: User (U) connects to server (S) through proxy (P), bypassing firewall restrictions (FW). Encrypted tunnel (Enc) prevents content inspection.}
+\label{fig:proxy}
+% \vspace{-0.2cm}
+\end{figure}
+
+With the evolution of censors, proxy protocols need more sophisticated designs to combat the detection mechanisms that we have mentioned. Whose idea we can conclude as:
+\begin{enumerate}
+    \item Encryption and Obfuscation
+    \item Camouflage
+\end{enumerate}
+
+\subsection{Encryption and Obfuscation}
+The idea of encryption comes in combat of passive inspections (typically attempt to decrypt), and obfuscation algorithms are additionally designed and put into use in order to reduce distinguishable characteristics of encrypted traffic.
+But as we talked about, unidentifiable encrypted connections (the ideal result of an obfuscation algorithm) can always be suspicious.
+Furthermore, from the perspective of security, the cipher suites that are adopted by those protocols are not always rigorously verified like mature SSL/TLS stack; from the perspective of engineering, we should better reuse mature solutions rather than reinvent the wheel.
+But those protocols always have a remarkable advantage, they can be stateless can be compatible with UDP forwarding.
+
+\subsubsection{Passive Detection}
+Generally speaking, the mechanism of encryption is just the combination of existing cipher suits, and obfuscation has multiple dimensions:
+\begin{itemize}
+    \item Manipulating the order of bytes stream in order to combat byte sequence analysis.
+    \item Insert padding bytes in the bytes stream in order to combat packet length analysis.
+    \item Alternating the order of sending packets in order to combat timing analysis.
+\end{itemize}
+
+\subsubsection{Active Probe}
+Target to those kinds of proxy servers, the active probe always evaluates servers' reactions and behaviors as we formerly mentioned.
+
+\subsection{Camouflage (Especially as HTTPS Traffic)}
+We discussed the advantages which TLS protocol stack can provide seamlessly; in this section we will focus on the mitigations that combat detection approaches.
+We will discuss it with Naiveproxy, one of the best practices of this idea in two perspectives, active probing and passive detection
+
+\subsubsection{Passive Detection}
+\begin{itemize}
+    \item In order to mitigate \textbf{TLS Fingerprinting}, naiveproxy utilizes the network stack of chromium, which is open source and widely adopted.
+    \item \textbf{Packet Length Analysis} can be combated with padding and dividing packets.
+    \item  With the utilization of Chromium's network stack, Naiveproxy is supposed not to expose any outstanding \textbf{behaviors} that differ from standard behaviors of Chromium.
+\end{itemize}
+
+In practice, we should notice that not only Web Browsers (and Webviews) have their own HTTPS implementation; some clients or libraries such as libcURL and OkHTTP also implement HTTPS methods based on TCP socket, so a client cannot be identified as a web browser does not mean that it is a TLS-based proxy client which tries to camouflage HTTPS connections.
+
+\subsubsection{Active Probe}
+After the active probing mechanism was revealed, most HTTPS-based protocols adopted combat which is called "Fallback".
+A valid packet that is initiated by proxy client should have a proxy header (Of course, it is encrypted and embedded in TLS payload) carried credential for authentication.
+When the authentication fails, it will be regarded as a malicious probe, the proxy server will forward it to a HTTP server behind.
+Such a HTTP can both forward it like a mirror Station or serve a HTTP content.
+That will make the proxy server become stealthy to censor and acts like a normal website or a mirror site.
+
+\begin{figure}[!h]
+    \centering
+    \include{figures/fallback}
+    \caption{Fallback: Proxy servers filter (P) unauthentic incoming traffic (P) (Probes) and forward it to a real HTTP Server (F) and forward authentic traffic (C) to destination (D)}
+    \label{fig:fallback}
+\end{figure}
+
+\subsection{Conclusion}
+In conclusion, the central of network censorship circumvention is camouflage or \textbf{Collateral freedom}.
+In practice, both sides, efforts of detection and circumvention use a combination of those techniques.
+For example, a protocol based on TLS should also consider its packet length characteristics.
+There are still some topics and remarkable technologies I cannot cover, such as identifying protocols with Deep Packet Inspection(DPI) in multiple OSI Layers and Machine Learning.
+I thought domain fronting used to be an outstanding idea which is one of the best practices of the idea.
+TOR provided Domain Fronting based meek bridge before,  but due to various factors such as this technology can also be abused to perform stealthy internet attacks, most CDN providers stopped the support (It also exhibits some temporal characteristics).
+Internet freedom is a significant topic, and though we focus on the technical details in this paper, we should recognize that it needs a collective effort to defend freedom, as it is a citizen's right that cannot be deprived.
+
+\bibliographystyle{ieeetr}
+
+\bibliography{ref}
+
+\appendix
+\section{Setting Up Proxy Server}
+In this appendix, we will elaborate on some technical details about our methodology.
+
+\subsection{Software Installation}
+To set up a remote proxy server, we need to log in the remote server through SSH and pull corresponding software from their official code repository since that software may not be available in the official package registries of most of the Linux distributions, we might be not able to manage in with package manager.
+
+\subsection{Issue a Valid SSL Certificate}
+For HTTPS-based protocols, we also need to obtain a valid SSL certificate issued by CA (We have discussed why we should not use self-signed certificates).
+It is possible to use a free SSL certificate that lasts 60 days issued by \href{https://letsencrypt.org/}{Let's Encrypt} or buy one from a CA (usually also a domain registrar), which can be valid longer.
+For a free SSL certificate, we can also use some tools to automate the process of renewal and installation.
+
+\subsection{Configuration}
+We made the sample configuration files available in folder \texttt{resources/config}. For more details, please refer to those projects' documents and the Linux man page or send an email to me.
+
+\appendix
+\section{Data Collection and Analysis}
+We have published the support code and put it in folder \texttt{resources/Code} at the same project. The manual can also be found in \texttt{resources/Manual}.
 

### 2024-11-20 resources/Code/Visualisation/entropy_statistics_visualization.py

@@ -8,41 +8,36 @@ def plot_temporal_entropy_statistic_of_protocol_in_temporal_domain(analyse: Pcap
     ts, data = calculate_entropy_per_packet(analyse)
     ax.plot(ts, data, label=analyse.protocol_name)
 
-def plot_entropy_statistic_in_temporal_domain(save_path:os.path, **kwargs:PcapAnalyse):
-    # fig, ax = plt.subplots()
-    # ax.set_xlim(0, 120)
-    # ax.set_ylim(0, 8)
-    # ax.set_xticks(np.arange(0, 120, 10))
-    # ax.set_yticks(np.arange(0, 8, 0.5))
-    # ax.set_title('Statistic of Entropy of single packet')
-    # for protocol_name, analyse in kwargs.items():
-    #     plot_temporal_entropy_statistic_of_protocol_in_temporal_domain(analyse, fig, ax)
-    # ax.legend()
-    # ax.set_xlabel('Time')
-    # ax.set_ylabel('Entropy')
-    # if not __debug__:
-    #     plt.savefig(save_path, format='png')
-    # plt.show()
+def plot_entropy_statistic_in_temporal_domain(save_path:os.path, split=False,**kwargs:PcapAnalyse):
     fig = plt.figure(figsize=(15, 20))
     fig.tight_layout()
     plt.subplots_adjust(hspace=0.2, wspace=0.3)
     fig.suptitle('Payload Length in Temporal Domain')
-    # lines = []
-    # labels = []
     for index, (protocol_name, analyse) in enumerate(kwargs.items()):
         # label = analyse.protocol_name
         ax = fig.add_subplot(2, 3, index + 1)
         ax.set_xlim(0, 120)
         ax.set_ylim(0, 8)
         ax.set_xticks(np.arange(0, 120, 10))
-        # ax.set_yticks(np.arange(0, 600, 100))
         ts, data = calculate_entropy_per_packet(analyse)
         line = ax.plot(ts, data, label=analyse.protocol_name)
-        # labels.append(label)
-        # lines.append(line)
         ax.set_title(f'{protocol_name}')
         ax.set_xlabel('Time')
         ax.set_ylabel('Entropy')
+    if not __debug__:
+        plt.savefig(save_path, format='png')
+    plt.show()
+
+def plot_single_temporal_entropy_statistic_of_protocol_in_temporal_domain(save_path:os.path, analyse:PcapAnalyse):
[…]

### 2024-11-20 resources/Code/Visualisation/length_statistics_visualization.py

@@ -23,6 +23,17 @@ def plot_occurrence_of_length(save_path: PcapAnalyse, **kwargs: os.path):
         plt.savefig(save_path, format='png')
     plt.show()
 
+def plot_single_occurrence_of_length(save_path: os.path, analyse: PcapAnalyse):
+    fig, ax = plt.subplots()
+    hist, bins = occurrence_histogram(analyse, 5)
+    ax.hist(hist, bins=bins)
+    ax.set_title(f'{analyse.protocol_name}')
+    ax.set_xlabel('Length')
+    ax.set_ylabel('Occurrence')
+    if not __debug__:
+        plt.savefig(save_path, format='png')
+    plt.show()
+
 # The temporal statistics of length for every packet for a single protocol
 # We should combine it to a plot in order to compare between different protocols
 def plot_length_statistic_of_protocol_in_temporal_domain(analyse: PcapAnalyse, fig, ax):
@@ -30,7 +41,7 @@ def plot_length_statistic_of_protocol_in_temporal_domain(analyse: PcapAnalyse, f
     ax.plot(ts, data, label=analyse.protocol_name)
 
 # The combination of all the protocols' graphs
-def plot_length_statistic_in_temporal_domain( save_path: os.path, **kwargs: PcapAnalyse):
+def plot_length_statistic_in_temporal_domain(save_path: os.path, **kwargs: PcapAnalyse):
     fig = plt.figure(figsize=(15, 20))
     fig.tight_layout()
     plt.subplots_adjust(hspace=0.2, wspace=0.3)
@@ -56,3 +67,18 @@ def plot_length_statistic_in_temporal_domain( save_path: os.path, **kwargs: Pcap
     if not __debug__:
         plt.savefig(save_path, format='png')
     plt.show()
+def plot_single_length_statistic_in_temporal_domain(save_path: os.path, analyse: PcapAnalyse):
+    fig, ax = plt.subplots()
+    ax.set_xlim(0, 120)
+    ax.set_ylim(0, 3000)
+    ax.set_xticks(np.arange(0, 120, 10))
+    # ax.set_yticks(np.arange(0, 600, 100))
+    ts, data = temporal_length_array(analyse)
+    line = ax.plot(ts, data, label=analyse.protocol_name)
+    ax.set_title(f'{analyse.protocol_name}')
+    ax.set_xlabel('Time')
+    ax.set_ylabel('Length')
+    if not __debug__:
+        plt.savefig(save_path, format='png')
+    plt.show()
+

### 2024-11-20 resources/Code/main.py

@@ -1,40 +1,75 @@
-from Visualisation.entropy_statistics_visualization import plot_entropy_statistic_in_temporal_domain
+from Visualisation.entropy_statistics_visualization import plot_entropy_statistic_in_temporal_domain, \
+    plot_single_temporal_entropy_statistic_of_protocol_in_temporal_domain
 from utils import get_pcap_file_path, get_result_file_path
 from Analyse.pcap_analyse import PcapAnalyse
 from Analyse.pcap_entropy_analyse import calculate_entropy_of_data, calculate_general_entropy
-from Visualisation.length_statistics_visualization import plot_occurrence_of_length, plot_length_statistic_in_temporal_domain
-
+from Visualisation.length_statistics_visualization import plot_occurrence_of_length, \
+    plot_length_statistic_in_temporal_domain, plot_single_occurrence_of_length, \
+    plot_single_length_statistic_in_temporal_domain
+import sys
 protocols = ['naiveproxy', 'trojan', 'shadowsocks', 'obfs4', 'https']
 
 analyses = [PcapAnalyse(get_pcap_file_path(protocol), protocol) for protocol in protocols]
 
+
+
 def main():
-    entropy_occurrence_statistic_and_analyse()
+    s = split()
+    entropy_occurrence_statistic_and_analyse(s)
 
-    length_statistic_in_temporal_domain()
+    length_statistic_in_temporal_domain(s)
 
-    entropy_statistic_in_temporal_domain()
+    entropy_statistic_in_temporal_domain(s)
 
     get_general_entropy()
 
-def entropy_occurrence_statistic_and_analyse():
+def split():
+    s = False
+    if len(sys.argv) > 1:
+        argument = sys.argv[1]
+        s = argument == '--split-output-figure' or argument == '-s'
+    return s
+
+def entropy_occurrence_statistic_and_analyse(split: bool):
     print('Start [entropy occurrence statistic and analyse]')
-    d, result_path = get_kwargs_and_result_path('occurrence_of_length')
-    plot_occurrence_of_length(result_path, **d)
+    d = get_kwargs()
+    if split:
+        for protocol_name, analyse in d.items():
+            result_path = get_result_file_path(f'occurrence_of_length_{protocol_name}')
+            plot_single_occurrence_of_length(result_path, analyse)
+            print(f'Plot saved at {result_path}')
+    else:
+        result_path = get_result_file_path('occurrence_of_length')
+        plot_occurrence_of_length(result_path, **d)
+        print(f'Plot saved at {result_path}')
[…]

### 2024-11-20 paper/include/fallback.tex
Try to fix CI by moving figures to include/
FIX: change \include{include/fallback} to \input{include/fallback}

--- 2024-11-20 paper/figures/fallback.tex
@@
 \begin{tikzpicture}[
-    scale=0.4, % Further reduced scale
-    node distance=2cm, % Further reduced distance
-    % user/.style={circle,draw,minimum size=0.6cm},
-    % attacker/.style={rectangle,draw,fill=red!20,minimum width=1cm,minimum height=0.7cm},
-    % server/.style={rectangle,draw,minimum width=1cm,minimum height=0.7cm}
+    scale=0.4,
+    node distance=2cm,
     censor/.style={rectangle,draw,fill=red!20,minimum width=1cm,minimum height=0.7cm},
@@
 ]
-    % Define nodes with shorter labels
-    % \node[user] (alice) {A};
-    % \node[attacker] (mitm) [right of=alice] {M};
-    % \node[server] (server) [right of=mitm] {S};
+
     \node[client] (client) {C};
@@
 
-    % Shorter arrows and smaller labels
-    % \draw[->,thick] (alice) to[bend left=20] node[above,font=\tiny] {Msg} (mitm);
-    % \draw[->,thick] (mitm) to[bend left=20] node[above,font=\tiny] {Mod} (server);
-    % \draw[->,thick] (server) to[bend left=20] node[below,font=\tiny] {Rsp} (mitm);
-    % \draw[->,thick] (mitm) to[bend left=20] node[below,font=\tiny] {Mod} (alice);
     \draw[->] (client) to node[above, font=\tiny] {Req} (proxy);

### 2024-11-24 paper/paper.tex
Try to fix CI by moving figures to include/
Correcting reference source
FIX: change \include{include/fallback} to \input{include/fallback}
fix Typos

@@
 \begin{abstract}
-This paper review and discussion the adversary between censorship and approaches to circumvent those restrictions from technical perspective
+This paper reviews and discusses the adversary between censorship and approaches to circumvent those restrictions from technical perspective
 \end{abstract}
@@
 Nowadays, most protocols (both TLS and non-TLS based) have widely adopted AES algorithms.
-    \item - There can be more chances when we consider the asymmetric-key exchange phases, which only happen when a TLS-based protocol tries to establish.
+    \item  There can be more chances when we consider the asymmetric-key exchange phases, which only happen when a TLS-based protocol tries to establish.
 For example, MITM Attack, but I will elaborate in the following module, which goes on “Active Probing” since it needs to intercept and tamper packets.
@@
 
-\subsection{The Active Detecion}
+\subsection{The Active Detection}
 Active detection can be used as a supplement, but it is not so widely adopted as passive inspection (But in authoritarian countries that have an extreme network censor it is adopted), the main reason is scanning, probing, and sniffing are always regarded as "sensible" activities and associated with suspicious Hack activities.
@@
 \centering
-\input{figures/mitm}
+\input{include/mitm}
 \caption{MITM attack: Attacker (M) intercepts messages between sender (A) and server (S).}
@@
 \centering
-\input{figures/proxy}
+\input{include/proxy}
 \caption{Proxy-based network bypass: User (U) connects to server (S) through proxy (P), bypassing firewall restrictions (FW). Encrypted tunnel (Enc) prevents content inspection.}
@@
     \centering
-    \include{figures/fallback}
+    \input{include/fallback}
     \caption{Fallback: Proxy servers filter (P) unauthentic incoming traffic (P) (Probes) and forward it to a real HTTP Server (F) and forward authentic traffic (C) to destination (D)}
@@
 
-\bibliography{ref}
+\bibliography{paper}
 

### 2024-12-02 paper/paper.tex
improve with the advices from professor

--- 2022-03-01 paper/paper.tex
@@
-% Do not change the section below
-% ============================================================================
-\documentclass[conference,compsoc,a4paper]{IEEEtran}
+\\documentclass[conference]{IEEEtran}
 \IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+%Template version as of 6/27/2024
 
-\usepackage{nimbusmononarrow}
-\usepackage[T1]{fontenc}
-
-\usepackage{balance}
-\usepackage{cite}
+% \usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{graphicx}
+% Graphic path
+% \graphicspath{{./pics/}}
 \usepackage{textcomp}
 \usepackage{xcolor}
+\usepackage{orcidlink}
+\usepackage{hyperref}
+\usepackage{multirow}
+\usepackage{float}
+\usepackage{tikz}
+\usetikzlibrary{positioning}
+\usepackage{textcomp}
+\usepackage{listings}
 \usepackage{subcaption}
-\usepackage{url}
+
+\lstset{
+    basicstyle=\ttfamily,
+    breaklines=true,
+    breakatwhitespace=true,
+    keepspaces=true,
+    columns=fullflexible,
+    showstringspaces=false,
+    % Prevent word splitting
+    % breakwords=true,
+    % allowbreak=true,
+    % postbreak=\mbox{\textcolor{red}{↪}},
+    % Optional: prevent hyphenation
+    % hyphenation=true
+}
 
@@
 
-\newcommand{\fixme}[1]{\textcolor{red}{[FIXME: #1]}}
-% ============================================================================
-
-% Add additionale LaTeX packages if needed here
-% ============================================================================
-\usepackage[%
-	detect-all,
-	binary-units=true,
-]{siunitx}
-\usepackage{booktabs}
-\usepackage{tikz}
-\usepackage{moeptikz}
-% ============================================================================
-
+% \usepackage[
+% backend=biber,
+% style=IEEEtran,
+% sorting=ynt
+% ]{biblatex}
+% \addbibresource{ref.bib}
 \begin{document}
 
-% Add paper title here, most likely you want to delete the \thanks{} macro
-% ============================================================================
-\title{Paper Title}
-% ============================================================================
+\title{The Eternal Adversary between Censor and Circumvention}
+\footnotesize
+% \textsuperscript{*}Note: Sub-titles are not captured for https://ieeexplore.ieee.org  and should not be used
+%\thanks{Identify applicable funding agency here. If none, %delete this.}
 
-% Update author information
-% ============================================================================
-\author{%
-	\IEEEauthorblockN{%
-		Your Name,
-		Advisor's Name\IEEEauthorrefmark{1}
-	}
-	\IEEEauthorblockA{%
-		\IEEEauthorrefmark{1}Chair of Network Architectures and Services,
-		Department of Informatics\\
-		Technical University of Munich, Germany\\
-		Email: your@mail.address, advisor@net.in.tum.de
-	}
-}
-% ============================================================================
-
+\author{\IEEEauthorblockN{1\textsuperscript{st} Guanru Chen}
+\IEEEauthorblockA{\textit{Technische Universität München} \\
+\textit{guanru.chen@tum.de \orcidlink{0009-0004-0715-910X}}}}
 \maketitle
 
-% Edit include/abstract.tex to write your paper's abstract
-% ============================================================================
 \begin{abstract}
-\input{include/abstract}
+This paper reviews and discussion the adversary between censorship and approaches to circumvent those restrictions from technical perspective.
+This paper discusses the current technologies in Aspect of Detection, Restriction, and Circumvention.
+We also actively collect, process, and visualize proxy traffic for obtaining supporting resources.
+We elaborate on the adversary on both sides, censor and circumvention and the current mainstream technologies about that.
 \end{abstract}
-% ============================================================================
 
-% List keywords of your paper in lower-case below
-% ============================================================================
 \begin{IEEEkeywords}
-software-defined networks, measurement, hight-speed networks
+Censorship, Firewall, Proxy, Encryption, TLS
 \end{IEEEkeywords}
-% ============================================================================
 
-% For each section of your chapter add one source file in the include folder
-% ============================================================================
-\input{include/introduction}
-\input{include/related_work}
-\input{include/formatting}
-\input{include/structure}
-\input{include/conclusion}
-% ============================================================================
+\section{Introduction}
+Restrictions of network connectivity are everywhere and are deployed for various reasons: companies use such technologies for security audits and the prevention of commercial secrets leakages, parents use them to control children's screen time, and regimes also deploy them on a large scale to stifle freedom of thought… However, there are some approaches that try to circumvent it.
+In this article, we discuss the adversity between the rivals by focusing on technologies and their evolution from a technical perspective.
+The primary idea of restriction is simple: as an Internet service provider (ISP), censors can drop a packet with specific criteria (such as destination IP, destination port, protocol in TCP/IP 5 tuple).
+The primary idea of a proxy is also simple: through an external server as a relay (or springboard) to reach the site blocked by the local network.
 
-% Put your references in the paper.bib file
-% ============================================================================
-\balance
+\section{Related Work}
+There are some existing works that discuss those technologies in specified aspects, such as TLS fingerprinting\cite{TLS_Fingerprinting}, active probing \cite{Active_Probing}, and analysis (or audition) of protocols \cite{shadowsocks_analysis} \cite{Trojan-Probe}.
+In this article, we intend to give an overview of these technologies with practical examples and real-world scenarios.
 
-\bibliographystyle{IEEEtran}
-\bibliography{paper}
-% ============================================================================
+\section{Methodology}
+We analyze typical protocols statically in our cloud servers and visualize the data.
+
+\subsection{Protocols that We Took Into Consideration}
+We chose typical protocols with different ideas:
+\begin{enumerate}
+    \item \href{https://shadowsocks.org}{Shadowsocks} (to be more specific, we use its newest rust-based implementation since it is still under active maintenance) and \href{https://gitlab.com/yawning/obfs4}{obfs4 bridge}, which represents the idea of encrypting and obfuscating.
+    \item \href{https://trojan-gfw.github.io/trojan/}{trojan-gfw} and \href{https://github.com/klzgrad/naiveproxy}{naiveproxy}, which are practices of the concept to camouflage HTTPS connection and to utilize TLS for security.
+    \item Plain HTTPS connection as a control group.
+\end{enumerate}
+
+\subsection{Set Up Proxy Server}
+We configure the remote proxy server and the corresponding dependencies since most server sides of the TLS-based protocols require an upstream Web Server to forward unauthorized web traffic, which is always considered an active probe.
+For more details about how it can be utilised by censor in practice, please refer to section \ref{sec:active_detection}.
+To make a TLS-based proxy server work, we must configure the proxy server program, the underlying "fallback" web server, and obtain a SSL certificate.
+For more about the mechanisms to combat active probing, especially the idea of "fallback", please refer to section \ref{sec:apc}.
+You can also find the sample configuration file in your repository.
+%See \ref{sec:config}.
+% We publish the notes and more technical details about the servers' configuration processes in the seminar repository.
+
+\subsection{Data Collection by Capturing}
+We use tcpdump \cite{tcpdump} to capture network traffic that flows through.
+
+\begin{lstlisting}[language=bash]
+    tcpdump -G <capture interval> -W 1 -w <protocol name>.pcap -i <network interface> -n dst host <ip> and dst port <port> and <transmission protocol> --print
+\end{lstlisting}
+
+Specifying the enclosed parameters accordingly provides flexibility to filter traffic and interact with it.
+
+\subsection{Processing and Analysis}
+We implement a simple Python script with an external library, dpkt\cite{dpkt}, which spares the time and work to decode recorded pcap files and strip negligible packet headers of corresponding lower OSI layers (we should focus on proxy traffic).
+In the analysis phase, we select two aspects (the most remarkable characteristics of encrypted protocols): entropy and packet length.
+Additionally, we should consider and measure their variations in the temporal domain.
+For TLS-based protocols, their TLS fingerprints introduce a new characteristic.
+The concept of TLS fingerprint is a combination of various factors according to the standard of SSL/TLS, key exchange algorithm, asymmetric encryption algorithm, symmetric encryption algorithm, MAC algorithm, SSL version, and further derived experimental features, e.g.
+session resumption, multiplex/HTTP2).
+Sorting and evaluating such versatile, statistically relevant data requires further consideration.
+However, we still implement some auxiliary functions to retrieve cipher suite information from client hello (if no encryption is applied).
+We have made the code available in the seminar repository.
+
+\section{The Censor}
+Almost all firewalls try to restrict only specific traffic, with interference in authorized connections as little as possible, so there is a need for mechanisms to distinguish between valid and invalid connection attempts.
+
+\subsection{The detection}\label{sec:detecion}
+Generally speaking, two kinds of approaches try to achieve this goal: passive tests, which try to analyze the existing data and figure out characteristics and patterns that make a disguised traffic identifiable, and active probes, which use measurements such as replay attack, tampering data, and man-in-the-middle attack.
+We discuss different approaches that try to distinguish "unauthorized" traffic.
+
+\subsection{The Passive Detection}
+Passive detection means that the censor analyzes the traffic that goes through their infrastructures (the "Infrastructures" are often gateways but should not be limited to gateways, for example, they can also use optical splitters to intercept traffic from fibers).
+When people use network tools such as tcpdump or CharlesProxy\texttrademark{} to check traffic, they do almost the same work with the censor, but beyond the idea, the tools that are adopted by censors can sometimes be much more sophisticated.
+Traffic can be inspected in multiple OSI Layers.
+Also, different Protocols can be analyzed with different measurements depending on their characteristics (for example, we can analyze a HTTPS traffic with the help of a MITM Attack).
+
+\subsubsection{Effort in decryption}
+ The most straightforward way to decide whether a connection is valid is to retrieve the carried payload and censor it.
+But in the age of AEAD (authenticated encryption with associated data) and HTTPS/SSL, it becomes complicated or can only be partially implemented in a very stringent condition like an attack that utilizes a classical vulnerability Heartbleed \cite{Heartbleed}.
+In most scenarios, it has been patched.
+ \begin{itemize}
+    \item  For symmetric-key algorithms, some extremely old encryptions before the advanced encryption standard (AES), such as single DES and RC-4 can be solved in a reasonable time.
+However, that is not a feasible approach because nowadays, most protocols (both TLS and non-TLS-based) have widely adopted AES algorithms.
+    \item There can be more chances when considering the asymmetric-key exchange phases, which only happen when a TLS-based protocol tries to establish.
+For example, MITM attack, for more detail about MITM, please refer to section \ref{sec:mitm}, which goes on “Active Probing” since it needs to intercept and tamper packets.
+Shor’s algorithm \cite{Shors_Algorithm} also provides a possibility to solve the question in polynomial time.
+Still, due to versatile technical limitations, it is generally not practical (such an existing quantum computer’s capability is like "it could tell you there is 70\% chance 15 = $3\times$5").
+ \end{itemize}
+
+\subsubsection{Entropy}
+Entropy is a remarkable factor in detecting a protocol, but it could not be the single factor since almost all ciphertexts have a high entropy.
+But it can be a factor together with the amount of traffic to make a preliminary decision whether a connection is suspicious and needs further investigation: high entropy (encrypted), long-lasting but non-HTTPS traffic can be an unauthorized attempt to connect, communicate, and transfer data between proxy client and proxy server.
+However the combination of those factors is not sufficient to determine it, or it introduces errors far beyond an acceptable range.
+We collect some of the typical encrypted protocols' traffic (both proxy protocols and genuine HTTPS protocol) and calculate its general entropy.
+Here is the overall entropy of each proxy protocol
+%we also verified our result with ent \cite{ent}.
+
+\begin{table}[h]
+\centering
+\caption{Average Entropy for Common Protocols}
+\resizebox{\columnwidth}{!}{
+\begin{tabular}{|l|lllll|}
+\hline
+\multirow{2}{*}{} & \multicolumn{5}{c|}{Protocol Name}                                                                                                   \\ \cline{2-6}
+                  & \multicolumn{1}{l|}{Shadosocks} & \multicolumn{1}{l|}{HTTPS} & \multicolumn{1}{l|}{NaiveProxy} & \multicolumn{1}{l|}{Trojan} & Obfs4 \\ \hline
+Entropy          & \multicolumn{1}{l|}{7.999}      & \multicolumn{1}{l|}{7.977} & \multicolumn{1}{l|}{7.992}      & \multicolumn{1}{l|}{7.858}  & 7.999 \\ \hline
+\end{tabular}%
+}
+\end{table}
+
+% Current Revisiting Process
+
+\subsubsection{TLS fingerprinting}
+For a TLS-based protocol, it additionally exposes fingerprints, that are mainly about offered and chosen cipher suits(key exchange, MAC, Key Length…).
+There have been many protocols that try to camouflage HTTPS connections by design.
+The HTTPS (to be more specific, TLS, Transport Layer Security on which HTTPS is built) protocol stack brings extra advantage in the prospect of security since it is designed and verified rigorously in terms of cryptography.
+For example, with TLS's implementation, developers can be exempt from worrying about protecting the server from reply attacks.
+Without security features provided by TLS, they must build a Bloom Filter on their own.
+But a Bloom Filter can also be a suspicious characteristic.
+On the other hand, a failed try to camouflage HTTPS traffic can be one of the most "deadly" remarkable characteristics \cite{TLS_Fingerprinting}.
+Except for the ciphers, there are many more factors that can be measured as fingerprints of HTTPS connections, which are initialized by a client, such as SSL/TLS version, certificates, multiplex (for HTTP/2), and more experimental features such as early data, TCP fast open (TFO).
+Such fingerprints can be used in conjunction with other factors, such as the packet length.
+We will elaborate on it later in the section \ref{section:cam}.
+There was a widely used Shadowsocks’ fork, ShadowsocksR, which tried to imitate HTTPS with an artificial SSL handshake.
+But when confronting a relatively mature and well-designed censor technology, those camouflages turned out to be a fatal vulnerability: it did not establish a real SSL connection, just attempts to make a fake handshake and attach an artificial HTTPS header.
+
+\subsubsection{Behavior}
+Behavior is a generic factor that covers the reaction of both client and server in different scenarios: how do they communicate?
+Do they send heartbeat packets to keep living?
+What happens in handshake phase?
+How do they exchange control instruction?
+These factors allow almost all professional routers to filter connections with OpenVPN or Wireguard protocol.
+But we focus on proxies such as obfs4 and Shadowsocks because most of the VPNs, together with SSH Tunnels, are not designed to have abilities to bypass censors (We are not going to talk about and consider some modified versions of OpenVPN, which are advertised as capable for censor bypassing, because they are always proprietary and do not follow an open standard).
+There are also behaviors worth researching and discussing, such as how servers react to active probes, see section \ref{sec:active_detection} "The Active Detection".
+
+\subsubsection{Packet length}
+The length of packets that carry the payload, header, and instructions of the proxy protocol is also a significant feature of protocols.
+An example is Trojan-gfw, which utilizes the TLS protocol stack but does not resize its packets.
+This leads to some packets with outstanding extreme lengths.
+The following figures that we depict show the occurrences of length respectively for each protocol.
+There are also length statistics of standard HTTPS traffic, which can be the control group.
+Naiveproxy uses padding and packet resizing to mitigate recognizing and categorization in the aspect of packet length.
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=0.4\textwidth, height=5cm]{pics/occurrence_of_length_trojan.png}
+%     \caption{The length-occurrence statistics of Trojan-gfw}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=0.4\textwidth, height=5cm]{pics/occurrence_of_length_https.png}
+%     \caption{The length-occurrence statistics of HTTPS}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=0.4\textwidth, height=5cm]{pics/occurrence_of_length_naiveproxy.png}
+%     \caption{The length-occurrence statistics of Naiveproxy}
+% \end{figure}
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}[b]{0.40\textwidth}
+        \includegraphics[width=\textwidth, height=4cm]{pics/occurrence_of_length_trojan.png}
+        \caption{Trojan}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.40\textwidth}
+        \includegraphics[width=\textwidth, height=4cm]{pics/occurrence_of_length_https.png}
+        \caption{HTTPS}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.40\textwidth}
+        \includegraphics[width=\textwidth, height=4cm]{pics/occurrence_of_length_naiveproxy.png}
+        \caption{Naiveproxy}
+    \end{subfigure}
+    \caption{Length-occurrence statistics}
+\end{figure}
+
+\subsubsection{Temporal domain (timing analysis)}
+As a connection is a dynamic process, how traffic varies in the temporal domain is worth researching.
+The timing analysis shows its significance, especially when a remarkable process happens such as a handshake.
+We depict The variations of different protocols in the temporal domain.
+It is worth noticing that because of Shadowsocks' nature (they use preset symmetric private key), it does not need key exchange and handshake (the connection itself can be stateless)
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.40\textwidth, height=4cm]{pics/temporal_statistic_of_entropy_shadowsocks.png}
+    \caption{The Entropy statistics of Shadowsocks in temporal domain}
+\end{figure}
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.45\textwidth]{temporal_statistic_of_entropy_https.png}
+%     \caption{The Entropy Statistics of HTTPS in Temporal Domain}
+%     \includegraphics[width=0.45\textwidth]{temporal_statistic_of_entropy_naiveproxy.png}
+%     \caption{The Entropy Statistics of Naiveproxy in Temporal Domain}
+%     \centering
+%     \includegraphics[width=0.45\textwidth]{temporal_statistic_of_entropy_trojan.png}
+%     \caption{The Entropy Statistics of Trojan-gfw in Temporal Domain}
+% \end{figure}
+
+\subsubsection{Other miscellaneous factors}
+There are also some miscellaneous outstanding characteristics, such as the structure of packets, special headers or bits (which is in even plaintext when a handshake happens).
+Classical VPNs and standard proxies that are not designed with the intention of providing censor bypass capability always have these characteristics.
+That's the reason most of industrial routers/gateways can distinguish and mark traffic as OpenVPN or Wireguard.
+
+\subsection{The active detection}\label{sec:active_detection}
+Active detection can be used as a supplement, but it is not so widely adopted as passive inspection (But in authoritarian countries that have an extreme network censor it is adopted), the main reason is scanning, probing, and sniffing are always regarded as "sensible" activities and associated with suspicious hack activities.
+But for national-level censors, who can control a large scale of malicious bot net.
+Because they have not only resources (of course, money from taxpayers) but also control the infrastructures of the backbone network.
+
+\subsubsection{Man in the middle attack}\label{sec:mitm}
+MITM attack is a common and practical way to decrypt TLS traffic due to the nature of asymmetric encryption:
+it is normal to practice MITM attacks in conjunction with downgrading attacks since network suppliers (for example ISPs, network administrators of enterprises or government) can always intercept, tamper, and mirror traffic which is carried by their links.
+Such attacks utilize the nature of the asymmetrical encryption and the key exchange process, which happens when a SSL/TLS channel tries to establish: the asymmetric encryption can guarantee the connection between peers is secure, but it cannot verify who the peer is.
+That means without further extra verification of the peer's identity (like a certificate issued by certificate authority CA), a man in the middle can easily fake the genuine peer and decrypt all the messages in your communication, as the following figure shows: through asymmetric encryption, there are two "secure" channels setup, but asymmetric encryption itself can not guarantee who the peer in another side of the "secure" channel is.
+
+\begin{figure}[!h]
+\centering
+\input{figures/mitm}
+\caption{MITM attack: Attacker (M) intercepts messages between client (C) and server (S).}
+\label{fig:mitm}
+% \vspace{-0.2cm}
+\end{figure}
+
+Furthermore, they can even attack at the level of certification suites, such as coercing all the devices that are allowed to access their local network install and trust their own root certificate.
+There are still means to solve that problem effectively: embed own certificate suites in apps (many applications, especially in the Android system, have adopted such “certificate pinning” mechanism.)
+
+\subsubsection{Replay attack targets to Non-TLS server}
+Protocols that do not use Authenticated Encryption with Associated Data (AEAD) algorithm are especially vulnerable when confronted with replay attacks.
+Without a reliable mechanism to calculate an associated message authentication code (MAC), authority and integrity cannot be guaranteed.
+Though the payload will still not leak.
+The control of the gateway gives ISPs (or other censors) the capabilities to block, intercept, surveillance, and tamper with any packet as long as the packet is carried over their network.
+So they can send probes, evaluate, and analyze how servers react to it: if servers’ reactions are specious, which means they have frequent, identifiable but "abnormal" behavior, for example, a server has different behavior when handling altered and not altered replay probe, because such behavior is stably distinguishable with other normal network services.
+Things can be even worse when the server cannot filter those replay attacks and treats it like a valid request and response.
+Because of the encryption, an attacker cannot really retrieve any content, but it is sufficient to identify and block the proxy server\cite{Active_Probing}.
+The worst case happens because of both the detailed implementation defect and the nature of "stream Cipher" (non-AEAD implementations).
+In the period around October 1.
+2018, a "sensitive" period, when the Chinese Communist Party regime celebrated their illegal seizure of power, they reinforced the firewall and probably for the first time put this new active probe technique into practice.
+That is indeed effective since Shadowsocks/R with stream cipher at that time was one of the most popular protocols and almost all the users reported they were affected.
+After that, these new techniques and their underlying mechanisms were, for the first time, recognized and uncovered by developers.
+There is some Mitigation of that: initially, stream ciphers (which means ciphers except AES-GCM and chacha20-poly1305 family) should be deprecated.
+As a mitigation, Bloom Filter is also adopted in those proxies (but the existence of Bloom Filter in the server side may even be a new feature).
+
+\subsubsection{Replay attack targets to TLS server}
+It is rational to browse the Internet with HTTPS protocol, though that is both highly encrypted and long-lasting.
+But active probing still has usages: its idea is not so cryptographic, yet more logical: check the server, it is suspicious when there is no real content to offer like a real web server (or something like WebDAV or git server, which also offers web access).
+We have further discussions later in the "Circumvention and Mitigation" section \ref{sec:apc}.
+% The approach to mitigating those kinds of probes is also straightforward, such as setting up a real web server that can offer dynamic or static web content(such as Nginx, or Apache).
+When the proxy server receives a probing, in other words, when it receives a HTTPS connection but cannot validate the payload, it forwards it to the web server and returns regular web content (developers call it "fallback").
+
+\subsection{Restriction}
+After traffic is identified, a censor can take measures to block or restrict it.
+It is about two questions:
+\begin{enumerate}
+    \item \textbf{How can a censor select the designated traffic as precisely as possible?}
+    \item \textbf{How can a censor impose a restriction on the designated traffic as precisely as possible?}
+\end{enumerate}
+There are versatile factors that can be the basis of restriction.
+The concrete approaches to the imposition of restrictions are also different.
+Generally speaking, all those techniques are highly associated with and based on the nature of the OSI layers.
+
+\subsubsection{TCP/IP 5 tuple}
+The primal idea of this problem is straightforward: use TCP/IP 5 tuple to specify a connection, as a system administrator does when they write an iptables statement.
+It is a Layer 3 (the Network Layer) and Layer 4 (the Transport Layer) based approach.
+
+\subsubsection{Block by SNI}
+Block a connection by SNI utilizes the nature of the HTTPS protocol stack, which lies on Layer 7 (the Application Layer).
+During the HTTPS handshake, a SNI delivers additional information to servers.
+This plaintext message cannot only be a factor in restrictions but also a defect in privacy since it is in plaintext and leaks the name of the website, to which a client wants to connect.
+So censors can block a HTTPS connection when the SNI is matched.
+It can also be mitigated with some experimental features such as ESNI and ECH.
+
+\subsubsection{Block by dropping packet}
+It is the most basic but feasible approach to restrict network access in a local network, and it makes a remote site at specific IP addresses unreachable.
+But it can be incapable in some scenarios, such as in authoritarian, even totalitarian states such as China or Iran, both all the ISPs that provide local network access and the physical channels (such as international submarine communication cables and fibers) are under control.
+That means if regimes decide to adopt an allow list, which means only allowing users in the local network to access local websites), all the protocols will be in vain because there is no side channel (Sometimes problems can be more than technical issues).
+
+\subsubsection{Reset TCP connection}
+This approach is based on the behavior of the TCP protocol stack: when a RST packet is received, the socket should stop the connection and exit.
+Stateless connection protocols like raw UDP are not affected.
+But generally speaking, those stateless protocols are not a practical mitigation because they are not widely used compared with TCP-based protocols, which means those family of protocols are not a good target to imitate and camouflage.
+There are further problems like not only QoS which is imposed by carriers (please see section \ref{sec:qos}), but also insufficient support for UDP packets transfer in unoptimized networks.
+
+\subsubsection{DNS pollution}
+That is also a well-known, widely and early adopted approach.
+Its basic mechanism is also straightforward: the original DNS server is unencrypted and will not be validated.
+The DNS system also has a decentralized nature that makes such pollution feasible: The downstream malicious DNS servers answer a query before the authentic Answer.
+Due to this known defect (and privacy weakness), DoH (DNS over HTTPS), DNSSec, and DoT (DNS over TLS)  are proposed as feasible mitigation.
+To this day, especially DoH is adopted, and also because of the decentralized essence, an anycast DNS server service (such as 1.1.1.1) cannot easily be blocked, but a censor can still disturb the query directly towards an authentic DNS Service located in the outside of the local network.
+
+\subsubsection{Quality of Service (QoS)}\label{sec:qos}
+Stateless-protocol-based communications (it does not need to establish a "connection") such as UDP and QUIC cannot be reset like TCP connections, but the censor (carrier) can also aggravate the quality of such connection by irregularly dropping packets, intentionally increasing the delay, make the transmission time become almost unacceptable.
+For stateful, connection-based protocols such as TCP, such interference can be more fatal.
+
+\section{Circumvention and Mitigation}\label{section:cam}
+Generally speaking, proxies and VPNs are based on the idea of side channel that gives unrestricted access to sites and addresses whose access is restricted in the local network.
+
+\begin{figure}[!h]
+\centering
+\input{figures/proxy}
+\caption{Proxy-based network bypass: user (U) connects to server (S) through proxy (P), bypassing firewall restrictions (FW). Encrypted tunnel (Enc) prevents content inspection.}
+\label{fig:proxy}
+% \vspace{-0.2cm}
+\end{figure}
+
+With the evolution of censors, proxy protocols need more sophisticated designs to combat the detection mechanisms that we have mentioned. Whose idea we can conclude as:
+\begin{enumerate}
+    \item Encryption and Obfuscation
+    \item Camouflage
+\end{enumerate}
+
+\subsection{Encryption and Obfuscation}
+The idea of encryption comes in combat of passive inspections (typically attempt to decrypt), and obfuscation algorithms are additionally designed and put into use in order to reduce distinguishable characteristics of encrypted traffic.
+But as we talked about, unidentifiable encrypted connections (the ideal result of an obfuscation algorithm) can always be suspicious.
+Furthermore, from the perspective of security, the cipher suites that are adopted by those protocols are not always rigorously verified like mature SSL/TLS stack; from the perspective of engineering, we should better reuse mature solutions rather than reinvent the wheel.
+But those protocols always have a remarkable advantage, they can be stateless can be compatible with UDP forwarding.
+
+\subsubsection{Passive detection}
+The mechanism of encryption is just the combination of existing cipher suits, and obfuscation has multiple dimensions:
+\begin{itemize}
+    \item Manipulating the bytes stream in order to combat byte sequence analysis.
+    \item Insert padding bytes in the stream in order to combat packet length analysis.
+    \item Alternating the order of sending packets in order to combat timing analysis.
+\end{itemize}
+
+\subsubsection{Active probe}
+Target to those kinds of proxy servers, the active probe always evaluates servers' reactions and behaviors as we formerly mentioned.
+
+\subsection{Camouflage (Especially as HTTPS Traffic)}
+We discussed the advantages which TLS protocol stack can provide seamlessly; in this section, we focus on the mitigations that combat detection approaches.
+We discuss it with the example of Naiveproxy, one of the best practices of this idea in two perspectives, active probing and passive detection
+
+\subsubsection{Passive detection}
+\begin{itemize}
+    \item In order to mitigate \textbf{TLS fingerprinting}, Naiveproxy utilizes the network stack of chromium, which is open source and widely adopted.
+    \item \textbf{Packet Length Analysis} can be combated by padding and dividing packets.
+    \item  With the utilization of Chromium's network stack, Naiveproxy is supposed not to expose any outstanding \textbf{behaviors} that differ from standard behaviors of Chromium.
+\end{itemize}
+
+In practice, we should notice that not only web browsers and Webviews have their own HTTPS implementations; some clients or libraries such as libcURL and OkHTTP also implement HTTPS methods based on TCP, so a client cannot be identified as a web browser does not mean that it is a TLS-based proxy client which tries to camouflage HTTPS connections.
+
+\subsubsection{Active probe}\label{sec:apc}
+After the active probing mechanism was revealed, most HTTPS-based protocols adopted combat which is called "Fallback".
+A valid packet that is initiated by the proxy client should have a proxy header carried credential for authentication.
+Of course, it is encrypted and embedded in TLS payload.
+When the authentication fails, it is regarded as a malicious probe.
+Then the proxy server forwards it to a HTTP server behind.
+Such a HTTP can both forward it like a mirror station or serve  HTTP content.
+That will make the proxy server become stealthy to censor and act like a normal website or a mirror site.
+
+\begin{figure}[!h]
+    \centering
+    \input{figures/fallback}
+    \caption{Fallback: Proxy servers filter (P) unauthentic incoming traffic (P) (Probes) and forward it to a real HTTP Server (F) and forward authentic traffic (C) to destination (D)}
+    \label{fig:fallback}
+\end{figure}
+
+\subsection{Conclusion}
+In conclusion, the central of network censorship circumvention is camouflage or \textbf{collateral freedom}.
+In practice, both sides, efforts of detection and circumvention use a combination of those techniques.
+For example, a protocol based on TLS should also consider its packet length characteristics.
+There are still some topics and remarkable technologies I cannot cover, such as identifying protocols with Deep Packet Inspection (DPI) in multiple OSI Layers and machine learning.
+I thought domain fronting used to be an outstanding idea which is one of the best practices of the idea.
+TOR provided domain fronting \cite{domainfronting} based meek bridge \cite{meek} before.
+Due to various factors such as this technology can also be abused to perform stealthy internet attacks, most CDN providers stopped the support.
+It also exhibits some temporal characteristics.
+Internet freedom is a significant topic, and though we focus on the technical details in this paper, we should recognize that it needs a collective effort to defend freedom, as it is a citizen's right that cannot be deprived.
+
+\bibliographystyle{ieeetr}
+
+\bibliography{ref}
+
+\appendix
+\section{Setting Up Proxy Server}
+In this appendix, we will elaborate on some technical details about our methodology.
+
+\subsection{Software installation}
+To set up a remote proxy server, we need to log in the remote server through SSH and pull corresponding software from their official code repository since that software may not be available in the official package registries of most of the Linux distributions, we might be not able to manage in with package manager.
+
+\subsection{Issue a valid SSL certificate}
+For HTTPS-based protocols, we also need to obtain a valid SSL certificate issued by CA (We have discussed why we should not use self-signed certificates).
+It is possible to use a free SSL certificate that lasts 60 days issued by \href{https://letsencrypt.org/}{Let's Encrypt} or buy one from a CA (usually also a domain registrar), which can be valid longer.
+For a free SSL certificate, we can also use some tools to automate the process of renewal and installation.
+
+\subsection{Configuration}\label{sec:config}
+We made the sample configuration files available in folder \texttt{resources/config}. For more details, please refer to those projects' documents and the Linux man page or send an email to me.
+
+\appendix
+\section{Data Collection and Analysis}
+We have published the support code and put it in folder \texttt{resources/Code} at the same project. The manual can also be found in \texttt{resources/Manual}.
 

### 2024-12-02 resources/Code/Visualisation/entropy_statistics_visualization.py

@@ -36,7 +36,7 @@ def plot_single_temporal_entropy_statistic_of_protocol_in_temporal_domain(save_p
     ts, data = calculate_entropy_per_packet(analyse)
     ax.plot(ts, data, label=analyse.protocol_name)
     ax.set_title(f'{analyse.protocol_name}')
-    ax.set_xlabel('Time')
+    ax.set_xlabel('Time (seconds)')
     ax.set_ylabel('Entropy')
     if not __debug__:
         plt.savefig(save_path, format='png')

### 2024-12-02 paper/paper.tex
fix redundant "\"
format fix

@@
-\\documentclass[conference]{IEEEtran}
+\documentclass[conference]{IEEEtran}
 \IEEEoverridecommandlockouts
@@
 
-\subsection{The detection}\label{sec:detecion}
+\subsection{The detection}\label{sec:detection}
 Generally speaking, two kinds of approaches try to achieve this goal: passive tests, which try to analyze the existing data and figure out characteristics and patterns that make a disguised traffic identifiable, and active probes, which use measurements such as replay attack, tampering data, and man-in-the-middle attack.
@@
 \multirow{2}{*}{} & \multicolumn{5}{c|}{Protocol Name}                                                                                                   \\ \cline{2-6}
-                  & \multicolumn{1}{l|}{Shadosocks} & \multicolumn{1}{l|}{HTTPS} & \multicolumn{1}{l|}{NaiveProxy} & \multicolumn{1}{l|}{Trojan} & Obfs4 \\ \hline
+                  & \multicolumn{1}{l|}{Shadowsocks} & \multicolumn{1}{l|}{HTTPS} & \multicolumn{1}{l|}{NaiveProxy} & \multicolumn{1}{l|}{Trojan} & Obfs4 \\ \hline
 Entropy          & \multicolumn{1}{l|}{7.999}      & \multicolumn{1}{l|}{7.977} & \multicolumn{1}{l|}{7.992}      & \multicolumn{1}{l|}{7.858}  & 7.999 \\ \hline

### 2024-12-02 paper/paper.tex
format fix
fix included tikz figures location
fix citation

@@
 \section{Related Work}
-There are some existing works that discuss those technologies in specified aspects, such as TLS fingerprinting\cite{TLS_Fingerprinting}, active probing \cite{Active_Probing}, and analysis (or audition) of protocols \cite{shadowsocks_analysis} \cite{Trojan-Probe}.
+There are some existing works that discuss those technologies in specified aspects, such as TLS fingerprinting\cite{TLS_Fingerprinting}, active probing \cite{Active_Probing}, and analysis (or audition) of protocols \cite{shadowsocks_analysis} \cite{Trojan_Probe}.
 In this article, we intend to give an overview of these technologies with practical examples and real-world scenarios.
@@
 \centering
-\input{figures/mitm}
+\input{include/mitm}
 \caption{MITM attack: Attacker (M) intercepts messages between client (C) and server (S).}
@@
 \centering
-\input{figures/proxy}
+\input{include/proxy}
 \caption{Proxy-based network bypass: user (U) connects to server (S) through proxy (P), bypassing firewall restrictions (FW). Encrypted tunnel (Enc) prevents content inspection.}
@@
     \centering
-    \input{figures/fallback}
+    \input{include/fallback}
     \caption{Fallback: Proxy servers filter (P) unauthentic incoming traffic (P) (Probes) and forward it to a real HTTP Server (F) and forward authentic traffic (C) to destination (D)}

### 2024-12-02 paper/paper.tex
fix citation
Do chores and clean some spell issues

@@
 \usepackage{graphicx}
-% Graphic path
-% \graphicspath{{./pics/}}
 \usepackage{textcomp}
@@
 
-% \usepackage[
-% backend=biber,
-% style=IEEEtran,
-% sorting=ynt
-% ]{biblatex}
-% \addbibresource{ref.bib}
 \begin{document}
@@
 \input{include/mitm}
-\caption{MITM attack: Attacker (M) intercepts messages between client (C) and server (S).}
+\caption{MITM attack: attacker (M) intercepts messages between client (C) and server (S).}
 \label{fig:mitm}
@@
     \input{include/fallback}
-    \caption{Fallback: Proxy servers filter (P) unauthentic incoming traffic (P) (Probes) and forward it to a real HTTP Server (F) and forward authentic traffic (C) to destination (D)}
+    \caption{Fallback: proxy servers filter (P) unauthentic incoming traffic (P) (Probes) and forward it to a real HTTP server (F) and forward authentic traffic (C) to destination (D)}
     \label{fig:fallback}

### 2024-12-22 paper/paper.tex
Do chores and clean some spell issues

--- 2024-12-02 paper/paper.tex
@@
 \usepackage{subcaption}
+\usepackage[english]{babel}
+\usepackage[autostyle, english = american]{csquotes}
+\MakeOuterQuote{"}
 
@@
 We configure the remote proxy server and the corresponding dependencies since most server sides of the TLS-based protocols require an upstream Web Server to forward unauthorized web traffic, which is always considered an active probe.
-For more details about how it can be utilised by censor in practice, please refer to section \ref{sec:active_detection}.
+For more details about how it can be utilized by censor in practice, please refer to section \ref{sec:active_detection}.
 To make a TLS-based proxy server work, we must configure the proxy server program, the underlying "fallback" web server, and obtain a SSL certificate.
@@
 Generally speaking, two kinds of approaches try to achieve this goal: passive tests, which try to analyze the existing data and figure out characteristics and patterns that make a disguised traffic identifiable, and active probes, which use measurements such as replay attack, tampering data, and man-in-the-middle attack.
-We discuss different approaches that try to distinguish "unauthorized" traffic.
+We discuss different approaches that try to distinguish unauthorized traffic.
 
 \subsection{The Passive Detection}
-Passive detection means that the censor analyzes the traffic that goes through their infrastructures (the "Infrastructures" are often gateways but should not be limited to gateways, for example, they can also use optical splitters to intercept traffic from fibers).
+Passive detection means that the censor analyzes the traffic that goes through their infrastructures (the Infrastructures are often gateways but should not be limited to gateways, for example, they can also use optical splitters to intercept traffic from fibers).
 When people use network tools such as tcpdump or CharlesProxy\texttrademark{} to check traffic, they do almost the same work with the censor, but beyond the idea, the tools that are adopted by censors can sometimes be much more sophisticated.
@@
     \item There can be more chances when considering the asymmetric-key exchange phases, which only happen when a TLS-based protocol tries to establish.
-For example, MITM attack, for more detail about MITM, please refer to section \ref{sec:mitm}, which goes on “Active Probing” since it needs to intercept and tamper packets.
+For example, MITM attack, for more detail about MITM, please refer to section \ref{sec:mitm}, which goes on Active Probing since it needs to intercept and tamper packets.
 Shor’s algorithm \cite{Shors_Algorithm} also provides a possibility to solve the question in polynomial time.
@@
 There are still some topics and remarkable technologies I cannot cover, such as identifying protocols with Deep Packet Inspection (DPI) in multiple OSI Layers and machine learning.
-I thought domain fronting used to be an outstanding idea which is one of the best practices of the idea.
-TOR provided domain fronting \cite{domainfronting} based meek bridge \cite{meek} before.
-Due to various factors such as this technology can also be abused to perform stealthy internet attacks, most CDN providers stopped the support.
+Domain fronting \cite{domainfronting} used to be an outstanding idea which is one of the best practices of the idea.
+TOR provided domain-fronting-based meek bridge \cite{meek} before.
+Due to various factors, such as the fact that this technology can also be abused to perform stealthy internet attacks, most CDN providers stopped the support.
 It also exhibits some temporal characteristics.
@@
 \section{Setting Up Proxy Server}
-In this appendix, we will elaborate on some technical details about our methodology.
+In this appendix, we elaborate on some technical details about our methodology.
 
@@
 \subsection{Configuration}\label{sec:config}
-We made the sample configuration files available in folder \texttt{resources/config}. For more details, please refer to those projects' documents and the Linux man page or send an email to me.
+We make the sample configuration files available in folder \texttt{resources/config}. For more details, please refer to those projects' documents and the Linux man page or send an email to me.
 
@@
 \section{Data Collection and Analysis}
-We have published the support code and put it in folder \texttt{resources/Code} at the same project. The manual can also be found in \texttt{resources/Manual}.
+We publish the support code and put it in folder \texttt{resources/Code} at the same project. The manual can also be found in \texttt{resources/Manual}.
 

### 2024-12-22 talk/include/slides.tex
Initialize presentation slides (sketchy)

@@
-\usepackage[utf8]{inputenc}
-\usepackage{tumcd/packages}
-\usepackage{tumcd/beamermods}
+% End video
 
-% For beamer mode (default):
-\author[S. G\"unther]{Stephan Günther}
-\title[Networking]{Something with Networking}
+% Header
+% \newcommand{\zwischentitel}{Seminar Presentation}
+% \newcommand{\leitthema}{Title}
+% End Header
 
-% Uncomment to add advisors for presentation in Oberseminar
-%\advisor{Herrmann B. Wolfgang}
+% Titlepage
+% \title{The Eternal Adversary between Censor and
+% Circumvention}
+% \author{Guanru Chen}
+% \newcommand{\presdatum}{December 2024}
+% \institute
+% {
+%   Technische Universität München\\
+% }
+% \subtitle{ Technical Perspective}
+% End Titlepage
 
-% Uncomment to add type for presentation in Oberseminar
-% Usage: \thesistype{intermediate | final}{bachelor | master | idp | gr}
-%\thesistype{intermediate}{gr}
+% Slides
+% \begin{document}
 
-% Uncomment to configure date in dd-mm-yyyy format
-%\newdate{date}{25}{05}{2017}
-%\date{\displaydate{date}}
+% 1. Slide: Titlepage
+% \begin{frame}
+% 	\titlepage
+% \end{frame}
 
-% Uncomment to add a venue to the title slide
-%\venue{International Conference on Conferencing 2018 \\ Garching b. München, Germany}
+% 2. Slide: TOC
+\begin{frame}
+   \frametitle{Contents and sections of presentation}
+   \tableofcontents[subsectionstyle=hide]
+\end{frame}
 
-% For lecture mode (use package option 'lecture'):
-%\lecture[GRNVS]{Grundlagen Rechnernetze und Verteilte Systeme}
-%\module{IN0010}
-%\semester{SoSe\,2016}
-%\assistants{Johannes Naab, Stephan Günther, Maurice Leclaire}
+% Further Slides
+% \section{Titles} 
+% \begin{frame}
+%    \frametitle{Title} 
+%    Each frame should have a title.
+% \end{frame}
 
-\usepackage{pgfpages}
-\usepackage{ifthen}
-% ============================================================================
-% jobname solution
-% ============================================================================
-\newif\ifsolution%
-\ifthenelse{\equal{\detokenize{notes}}{\jobname}}{%
-\setbeameroption{show notes on second screen=bottom}
-\setbeamercolor{note page}{bg=white, fg=black}
-\setbeamercolor{note title}{bg=white!95!black, fg=black}
-}{
+\section{Prologue}
+\begin{frame}
+    % \frametitle{Prologue}
+    \begin{quote}
+        ``Life is dear, love is dearer. Both can be given up for freedom.`` \\
+        --- Sandor Petöfi
+    \end{quote}
+
+\end{frame}
+
+\section{Methods}
+\subsection{Data Collection}
+\begin{frame}
+Some common ways to collect network traffic in different OSI layers
+\small
+\begin{itemize}
+    \item HTTP(s) Proxies like Charles Proxy, fiddler, and Proxyman, are widely used in web debugging. When you open the developer tool in your browser, you are actually analyzing network traffic. 
+    \item Packet capture tools that integrated with systems' network stack. The most famous and classic example is TCPDump and Wireshark.
+    There is a new remarkable approach in the Linux platform called eBPF (extended Berkeley Packet Filter), which is the successor of the classic BPF (Berkeley Packet Filter).
+It is an interesting and popular topic that is worth further investigation.
+For portability reasons, in our research, we still use the classical one.
+    \item Physical layer collection needs more special equipment, such as optical splitters and optical fiber detectors, that makes it possible to capture modulated physical signals.
+It is not so common, but it can still be utilized by national agencies.
+\end{itemize}
+
+\end{frame}
+
+% \begin{frame}\frametitle{Lists with Pause}
+%    \begin{itemize}
+%       \item Introduction to  \LaTeX \pause 
+%       \item Second bullet point \pause 
+%       \item And a third one \pause 
+%       \item The last one
+%    \end{itemize} 
+% \end{frame}
+
+% \begin{frame}{Use TCPDump Tool}
+% \begin{lstlisting}[language=bash]
+%     tcpdump -G <capture interval> -W 1 -w <protocol name>.pcap -i <network interface> -n dst host <ip> and dst port <port> and <transmission protocol> --print
+% \end{lstlisting}
+% Specifying the enclosed parameters accordingly provides flexibility to filter traffic and interact with it.
+% \end{frame}
+
+\subsection{Use TCPDump \cite{tcpdump} Tool}
+\begin{frame}[fragile]
+% \frametitle{Use TCPDump \cite{tcpdump} Tool}
+    TCPDump can capture, filter, and store designated traffic with given parameters. For more detail, please refer to its \href{https://www.tcpdump.org/}{manual}
+   \lstset{language=bash, basicstyle=\small \ttfamily, showspaces=false,   showtabs=false, tab= , keywordstyle=\bfseries,     showstringspaces=false, framexleftmargin=5mm, frame=single,     numbers=left,
+    numberstyle=\tiny,
+    stepnumber=1,
+    numbersep=5pt,
+    texcl=true, 
+    breaklines=true,
+    breakatwhitespace=true,
+    keepspaces=true,
+    columns=fullflexible,}
+    \begin{lstlisting}
+    tcpdump -G <capture interval> -W 1 -w <protocol name>.pcap -i <network interface> -n dst host <ip> and dst port <port> and <transmission protocol> --print
+    \end{lstlisting}
+    Specifying the enclosed parameters accordingly provides flexibility to filter traffic and interact with it.
+    It is possible to automate the process in order to collect larger-scale datasets.
+\end{frame}
+
+\subsection{Data Analysis and Plot}
+\begin{frame}
+% \frametitle{Data Analysis and Plot}
+
+\small
+Regarding passive (static) traffic analysis, we consider these factors: packet length, entropy, TLS fingerprint (if it has one), and those factors in the temporal domain.
+We should retrieve encrypted TCP payload from captured Ethernet frames first. 
+For analysis, we use library dpkt \cite{dpkt} and for visualization we use \href{https://matplotlib.org/}{matplotlib}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.35]{pics/plot.png}
+    \caption{\tiny A sample plot of Shadowsocks protocol.}
+    \label{fig:enter-label}
+\end{figure}
+
+\end{frame}
+
+\subsection{Server Configuration}
+\begin{frame}
+    % \frametitle{Server Configuration}
+
+    A few configurations may be needed to set up a proxy server.
+
+    \begin{itemize}
+    \item Install the server-side software, use package manager if possible.
+    \item Basic configuration. It will be required for almost all proxy protocols, in which you provide basic information, e.g. address, port to listen, and credentials for authorization.  
+    \item Obtain a SSL certificate if TLS should be used and maintain it e.g. renew it timely and adapt security response.
+    \item Set up a fallback server (more details of fallback we will discuss later in section \ref{sec:fallback}).
+    \end{itemize}
+\end{frame}
+
+\subsection{Protocols}
+\begin{frame}
+    % \frametitle{Protocols to Research}
+    We choose some typical protocols according to their features.
+    \begin{table}[h]
+    \begin{tabular}{|c|c|c|c|}
+      \hline
+      \diagbox{Protocol}{Feature} & TLS & Packet Length Padding & Fallback \\ \hline
+      Shadowsocks\cite{Shadowsocks} & \texttimes & \checkmark & \texttimes \\ \hline
+      Obfs4\cite{Obfs4} & \texttimes & \checkmark & \texttimes \\ \hline
+      Trojan\cite{Trojan_gfw} & \checkmark & \texttimes & \checkmark \\ \hline
+      Naiveproxy\cite{Naiveproxy} & \checkmark & \checkmark & \checkmark \\ \hline
+    \end{tabular}
+    \end{table}
+\end{frame}
+
+\subsection{Technical Details}
+\subsection{Fallback}\label{sec:fallback}
+\begin{frame}
+    % \frametitle{Fallback}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.20]{pics/fallback.png}
+        \caption{How fallback works in combat of probe \cite{Trojan-Probe}}
+        \label{fig:fallback}
+    \end{figure}
+\end{frame}
+
+\subsection{Supportive resources}
+\begin{frame}
+% \frametitle{Supportive Resources}
+    We publish related files in \href{https://gitlab.lrz.de/tuinh09/teaching/scni/repos/2024ws-hn/u157}{the project's repository}
+    \begin{itemize}
+        \item Configuration snippets can be found under folder \texttt{resources/Config}. "$<>$" enclosed values should be replaced accordingly.
+        \item Manuals and notes are under folder \texttt{resources/Manual}.
+    \end{itemize}
+
+\end{frame}
+
+\section{Topics}
+\subsection{Entropy}
+\begin{frame}
+    % \frametitle{Entropy}
+    The entropy can be calculated as $H = -\sum_{i=1}^{n} p_i \log_2(p_i)$. It represents how disordered a message is. Highly encrypted messages are near to random data.
+    It is also practical to consider the variation of entropy in the clock domain.
+    \begin{table}[h]
+    \centering
+    \caption{Average entropy for common protocols}
+    \resizebox{\columnwidth}{!}{
+        \begin{tabular}{|l|lllll|}
+        \hline
+        \multirow{2}{*}{} & \multicolumn{5}{c|}{Protocol Name}                                                                                                   \\ \cline{2-6} 
+                          & \multicolumn{1}{l|}{Shadowsocks} & \multicolumn{1}{l|}{HTTPS} & \multicolumn{1}{l|}{NaiveProxy} & \multicolumn{1}{l|}{Trojan} & Obfs4 \\ \hline
+        Entropy          & \multicolumn{1}{l|}{7.999}      & \multicolumn{1}{l|}{7.977} & \multicolumn{1}{l|}{7.992}      & \multicolumn{1}{l|}{7.858}  & 7.999 \\ \hline
+        \end{tabular}%
     }
+    \end{table}
+\end{frame}
 
-% TeXLive 2018 compatibility: https://tex.stackexchange.com/questions/426088/texlive-pretest-2018-beamer-and-subfig-collide
-\makeatletter
-\let\@@magyar@captionfix\relax
-\makeatother
+\subsection{Packet Length}
+\begin{frame}
+    % \frametitle{Packet Length}
+
+    % \small
+    Packet length is a significant factor in a protocol. Specifically, we should only consider its payload (i.e. Server Data Unit).
+    When using statistical methods to inspect it, an outlier can be remarkable. For example, as is shown in the paper, the Trojan protocol does not adopt a long packet resizing mechanism.
+\begin{figure}[H]
+    \centering
+        \includegraphics[scale=0.45]{pics/occurrence_of_length_trojan.png}
+    \caption{Length-occurrence statistics}
+\end{figure}
+\end{frame}
+
+\subsection{TLS Fingerprinting}
+\begin{frame}
+    % \frametitle{TLS Fingerprinting}
+
+    \small
+    As the SSL/TLS handshake happens in most plain text, the features of such a connection can be identified.
+For example, \texttt{TLS\_ECDHE\_RSA\_WITH\_CHACHA20\_POLY1305\_SHA256} shows cipher suites, both symmetric and asymmetric, hash function, and key exchange algorithm; they are typical TLS fingerprints.
+Besides, there are further features such as SSL versions and certificates.
+    All these factors composite a vector that can be categorized by algorithms (machine learning is needed).
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.15]{pics/TLS_Handshake.png}
+        \caption{\small TLS handshaking \cite{TLS_handshake}}
+        \label{fig:fallback}
+    \end{figure}
+\end{frame}
+
+\subsection{SNI/CH technologies}
+\begin{frame}
+    % \frametitle{SNI/CH Technologies}
+
+    In SSL/TLS handshaking processes, there is a remarkable phase, client hello (CH), that provides more information for the server along with TCP/IP 5 tuple and domain name, which will be especially useful when CDN or reverse proxy is enabled.
+    But it is firstly designed without taking privacy into consideration, so the primeval version of CH is in plain text, which exhibits information about the connection and makes the SNI-based block possible.
+    It has successors that try to mitigate the privacy defect, called eSNI and ECH, whose e stands for encrypted, but they are not widely adopted yet.
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.25]{pics/SNI_Block.png}
+        \caption{\small SNI based block \cite{SNI_block}}
+        \label{fig:fallback}
+    \end{figure}
+\end{frame}
+
+% \section{Colors}
+% \begin{frame}
+%    \frametitle{An Overview of TUM's Colors}
+%    \tiny{Color blue sRGB 100\%: 0-101-189} \\
+%    \colorbox{tumcolor-blue}{}{}  \\
+%    \vspace{0.5cm}
+%    \tiny{Color green sRGB 100\%: 162-173-0} \\
+%    \colorbox{tumcolor-green}{}{} \\
+%    \vspace{0.5cm}
+%    \tiny{Color light grey sRGB 100\%: 218-215-203} \\
+%    \colorbox{tumcolor-lightgrey}{}{} \\
+%    \vspace{0.5cm}
+%    \tiny{Color orange sRGB 100\%: 227-114-34} \\
+%    \colorbox{tumcolor-orange}{}{} \\
+%    \vspace{0.5cm}
+% \end{frame}
+
+\section{Conclusion}
+\begin{frame}
+    % \frametitle{Conclusion}
+    In conclusion, the central of network censorship circumvention is camouflage or \textbf{collateral freedom}. In practice, both efforts are based on the nature of OSI layers.
+    We can neither cover all the topics nor dive deep into all subdomains. This project gives an overview of these technologies.
+\end{frame}
+
+\section{Afterword}
+\begin{frame}
+    % \frametitle{Afterword}
+    \small
+    After finishing this project, I thought a lot and put some of my thoughts in the afterword out of my selfishness.
+    All technologies will not stay in academia but will finally enter the real world and be entangled with "impure" factors like ethics, society, and the environment.
+
+    So I believe that as technicians (or technicians in the future), we should have a sense of social responsibility and ethics, especially when we are dealing with technology.
+And that is what I demand myself.
+
+    After all, I hope that everyone can recognize and understand Freedom of speech (including but not limited to Internet freedom) is all the citizens' right, that can never be deprived.
+
+   \begin{figure}
+      \includegraphics[scale=0.05]{pics/XiaoboLiu_Nobel} 
+      \caption{Dr. Xiaobo Liu, Nobel Peace Prize winner of 2010\cite{Dr_xiaobo_liu}}
+   \end{figure}
+
+\end{frame}
+
+% \subsection{Code Listings} 
+% % The [fragile] is important for listings!
+% \begin{frame}[fragile]
+%    \frametitle{Don't Ever Bore the Audience with Code Listings}
+%    \lstset{language=C, basicstyle=\small \ttfamily, showspaces=false, showtabs=false, tab= , keywordstyle=\bfseries, showstringspaces=false, framexleftmargin=5mm, frame=single, numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt, texcl=true}
+%    \begin{lstlisting}[caption={Especially when they are erroneous},frame=tlrb]
+% #include <stdio.h>
+
+% int main(void)
+% {
+%   printf("Hallo Welt\n");
+%   while(1);
+%   return 0;
+% }
+%    \end{lstlisting}
+% \end{frame}
+
+% \begin{frame}[allowframebreaks]
+% \frametitle{Bibliography}
+%     \printbibliography
+% \end{frame}
+
+% \end{document}

### 2024-12-29 talk/include/slides.tex
Update and complete slides.tex

@@
 
-\section{Topics}
+\section{Detect, filter and categorize traffics}
+\begin{frame}
+    Passive detection analyzes the packets with a combination of multiple factors, such as \textbf{entropy}, \textbf{packet length}, and \textbf{TLS fingerpeints} (If TLS is used).
+    A connection can also be considered and analyzed in the clock domain.
+
+    Active detection furthermore requires the censors to intercept, tamper, and manipulate (mostly replay) packets.
+Such as sending probes (replaying modified or unmodified previous packets) and trying to implement famous \textbf{Man in the middle attack}.
+\end{frame}
+
 \subsection{Entropy}
@@
     \end{figure}
+\end{frame}
+
+\section{Block technologies}
+\begin{frame}
+    Generally, three ideas for blocking traffic are associated with the nature of network layers.
+    \begin{enumerate}
+        \item Drop packets, the layer 3 approach.
+        \item Reset TCP connections, based on TCP connections' stateful nature.
+        \item DNS pollution, raw DNS implementations without authentication and encryption will be vulnerable.
+    \end{enumerate}
+\end{frame}
+
+\subsection{Factors for blocking designated connections}
+\begin{frame}
+    \begin{itemize}
+        \item Using TCP/IP 5 tuple to specify a connection, as a system administrator does when they write an iptables statement.
+It is a layer 3 (the Network Layer) and layer 4 (the Transport Layer) based approach.
+        \item Block a connection by SNI utilizes the nature of the HTTPS protocol stack, which lies on layer 7 (the Application Layer).
+It can also be mitigated with some experimental features such as ESNI and ECH.
+    \end{itemize}
+\end{frame}
+
+\section{Circumvention technologies}
+\begin{frame}
+    As the title says, in the adversary between detection and circumvention, the opposite technologies are always associated with each other, which means they are always designed to combat each other.
+    For passive detection, there are mitigations:
+    \begin{itemize}
+    \item Manipulating the bytes stream in order to combat \textbf{byte sequence analysis}.
+    \item Insert padding bytes in the stream in order to combat \textbf{packet length analysis}.
+    \item Alternating the order of sending packets in order to combat textbf{timing analysis}.
+    \end{itemize}
+
+    For active detection
+    \begin{itemize}
+    \item In order to mitigate \textbf{TLS fingerprinting}, Naiveproxy utilizes the network stack of chromium, which is open source and widely adopted.
+    \item \textbf{Packet Length Analysis} can be combated by padding and dividing packets.
+    \item  With the utilization of Chromium's network stack, Naiveproxy is supposed not to expose any outstanding \textbf{behaviors} that differ from standard behaviors of Chromium.
+\end{itemize}
+
 \end{frame}

### 2025-01-14 review/review.tex
update sketch of review

\documentclass[a4paper,9pt]{scrartcl}
\usepackage{amssymb, amsmath} % needed for math
\usepackage[utf8]{inputenc}   % this is needed for umlauts
\usepackage[USenglish]{babel} % this is needed for umlauts
\usepackage[T1]{fontenc}      % this is needed for correct output of umlauts in pdf
\usepackage[margin=2.5cm]{geometry} %layout
\usepackage{hyperref}         % hyperlinks
\usepackage{color}
\usepackage{framed}
\usepackage{enumerate, enumitem}  % for advanced numbering of lists
\usepackage[autostyle,english=american]{csquotes}
\MakeOuterQuote{"} % for enquote

\newcommand\titletext{Peer-Review of\\"Advancing European Railway Systems: A Transition to Unified Control with ERTMS, ETCS, and 5G"}

\title{\titletext}
\author{Guanru Chen}

\hypersetup{
  pdfauthor   = {Guanru Chen},
  pdfkeywords = {peer review},
  pdftitle    = {Lineare Algebra}
}

\usepackage{microtype}

\begin{document}
\maketitle
\section{Introduction}
This is the peer review of the seminar paper \textit{Advancing European Railway Systems: A Transition to Unified Control with ERTMS, ETCS, and 5G}, which discusses the railway control system adopted by European railways and the prospect of 5G's practical usage in this domain. It also lists multiple implementations by country together with figures. It also covers the unified standards within the European Union and their evolution, such as the adoption of new mobile network standards. The last section of the paper shows the potential future of the combination and integration of 5G technology in European railway systems and the associated topics (improvement, feasibility, and security)

\section{Summary of the Content}
\subsection{Section 1. Introduction}
It briefly introduces the idea and development of several unified standards (ERTMS and ETCS) and gives an overview of the deployment of mobile networks in railway systems.
\subsection{Background information}
It lists some typical railway controlling standards and mechanisms with technical data. It also makes comparisons while taking real-world production factors into consideration.
\begin{enumerate}[label=(\Alph*)]
    \item Germany
    \begin{enumerate}[label=(\Roman*),ref=(\Alph{enumi}-\Roman*)]
        \item The Punktförmige Zugbeeinflussung (PZB) Standard
        \item The Linienzugbeeinflussung/Linienförmige Zugbeeinflussung (LZB) Standard
    \end{enumerate}
    \item France
    \begin{enumerate}[label=(\Roman*),ref=(\Alph{enumi}-\Roman*)]
        \item Trackside signaling
        \item Transmission Voie-Machine (TVM)
    \end{enumerate}
    \item Finland
    \begin{enumerate}[label=(\Roman*),ref=(\Alph{enumi}-\Roman*)]
        \item Junakulunvalvonta (JKV)
    \end{enumerate}
\end{enumerate}

\subsection{ERTMS and ETCS}
It introduces the concept of ERTMS and ETCS and shows some technical details with figures. And discuss the current status of the deployment of mobile network technologies, especially the LTE standard in these control systems.
The last paragraph of this section proposes the most significant idea, adopting 5G for railway systems. It discusses its feasibility, prospects, and advantages. Besides it mentions the security and compatibility concerns. It shows a real-world example with Hamburg's train station and surrounding areas.

\subsection{Conclusion}
This section concludes the prospects of the former topics and shows the prospects for the adoption of new 5G technologies.

\section{Overall Feedback}
It proposed a very innovative and practical topic combining computer network and telecom technologies with a real-world production scenario.
But I think the contents of 5G topic in the last section need to be ordered and rearranged into multiple subsections, or it should be extracted to a standalone section.
And there are more topics worth discussing, such as migrating to the new 5G technology-based control system, infrastructure requirements, and software support.
It is also remarkable that the authors are good at English writing, and it has almost no grammar mistakes (much better than I do).
I think it should focus more on 5G technologies, not only on showing details of previous railway control systems that are not even so digitalized (but I don't mean it should be completely eliminated for comparison).
In terms of organization and structure, it lacks a comparison of related works.

\section{Major Remarks}
\begin{itemize}
    \item \enquote{designated as ATP-VR/RHK, which is derived from Alstom’s
EBICab 900 technology.} - need citation.
\end{itemize}

\section{Minor Remarks}

\end{document}

### 2025-02-13 paper/paper.tex
minimum plot and text fix for rigor (thanks for the professor, who point out my mistake in data plotting)

@@
 An example is Trojan-gfw, which utilizes the TLS protocol stack but does not resize its packets.
-This leads to some packets with outstanding extreme lengths.
+This leads to characteristics, which has a recognizable pattern in the temporal domain (a burst of long packets).
 The following figures that we depict show the occurrences of length respectively for each protocol. 
@@
     \begin{subfigure}[b]{0.40\textwidth}
-        \includegraphics[width=\textwidth, height=4cm]{pics/occurrence_of_length_trojan.png}
+        \includegraphics[width=\textwidth, height=4cm]{pics/temporal_statistic_of_length_trojan.png}
         \caption{Trojan}
@@
     \begin{subfigure}[b]{0.40\textwidth}
-        \includegraphics[width=\textwidth, height=4cm]{pics/occurrence_of_length_https.png}
+        \includegraphics[width=\textwidth, height=4cm]{pics/temporal_statistic_of_length_https.png}
         \caption{HTTPS}
@@
     \begin{subfigure}[b]{0.40\textwidth}
-        \includegraphics[width=\textwidth, height=4cm]{pics/occurrence_of_length_naiveproxy.png}
+        \includegraphics[width=\textwidth, height=4cm]{pics/temporal_statistic_of_length_naiveproxy.png}
         \caption{Naiveproxy}

### 2025-02-13 resources/Code/Analyse/pcap_length_analyse.py
final revision before publish: minimum plot histgram fix in code.

@@ -28,17 +28,17 @@ import numpy as np
 def occurrence_histogram(analyse: PcapAnalyse, delta: int):
     occurrences = []
     for _, payload in analyse.tcp_payload_with_timestamp:
-        occurrences.append(len(payload))
+        l = len(payload)
+        # Filter the zero sized packets
+        if l > 0:
+            occurrences.append(len(payload))
     assert len(occurrences) > 0, f'Unexpected empty TCP payload in {analyse.pcap_file_name}'
     max_l = max(occurrences)
     min_l = min(occurrences)
     # Prepare np array for plotting
-    # The data in first row is length in y-axis
-    # The data in second row is occurrences in x-axis
-    len_bin = trunc((max_l - min_l) / delta)
-    bins = np.linspace(min_l, max_l)
 
-    return np.histogram(occurrences, bins=bins)
+    bins = np.linspace(0, max_l, 60)
+    return occurrences, bins
 
 def temporal_length_array(analysis: PcapAnalyse):
     t = analysis.retrieve_tcp_payload_or_timestamp(Choice.TIME_STAMP)

### 2025-02-13 resources/Code/Visualisation/length_statistics_visualization.py

@@ -15,7 +15,10 @@ def plot_occurrence_of_length(save_path: PcapAnalyse, **kwargs: os.path):
         hist, bins = occurrence_histogram(analyse, 5)
         # ax.set_xlim([0, max(bins)])
         # ax.set_xticks(np.arange(0, max(bins), 500))
-        ax.hist(hist, bins=bins)
+        ax.hist(hist,
+                bins=bins,
+                color='skyblue',
+                alpha=0.7)
         ax.set_title(f'{protocol_name}')
         ax.set_xlabel('Length')
         ax.set_ylabel('Occurrence')
@@ -26,7 +29,10 @@ def plot_occurrence_of_length(save_path: PcapAnalyse, **kwargs: os.path):
 def plot_single_occurrence_of_length(save_path: os.path, analyse: PcapAnalyse):
     fig, ax = plt.subplots()
     hist, bins = occurrence_histogram(analyse, 5)
-    ax.hist(hist, bins=bins)
+    ax.hist(hist,
+            bins=bins,
+            color='skyblue',
+            alpha=0.7)
     ax.set_title(f'{analyse.protocol_name}')
     ax.set_xlabel('Length')
     ax.set_ylabel('Occurrence')

### 2025-03-10 review/review.tex
Purge review stuffs for privacy and copyright considerations

@@
 
+\section{Strengths}
+It proposed a very innovative and practical idea that combines computer network and telecom technologies with a real-world production scenario.
+It provides abundant real-world examples and clear figures.
+It also gives a detailed, comprehensive overview of the current railway control system in Europe with comparisons (But I think it should be more focused on introducing 5G technology to these systems).
+the written English and grammar of the paper is good (much better than mine).
+
+\section{Weaknesses}
+As a seminar paper in aspect of Internet and security, it should be more focused on 5G (or generally speaking, the network and telecom technologies) itself.
+The author spends too much attention and length in the former non-digitalized railway control system, which is not the main focus of the paper.
+The author should also provide more detailed information about the topic itself, i.e. deploying, migrating and integrating 5G technology in railway system.
+The topic and idea is still potential and worth to be further explored, but the organization and content of the paper may need to be improved.
+
+\section{Questions to the author}
+\begin{itemize}
+\item What are the main challenges and difficulties in adopting 5G technology in railway system?
+
+\item In confront of these difficulties, what are the potential solutions and strategies?
+
+\item In the phase of migrating new technologies, how can man guarantee that the old and new system can cooperate?
+
+\item In the proposed model of 5G powered railway system in the surrounding area of hamburg, you mention a mechanism of arranging, scheduling and cooperating is needed, can you provide more details about that?
+
+\end{itemize}
+
 \section{Overall Feedback}
@@
 
-\section{Major Remarks}
+\section{Corrections}
 \begin{itemize}
@@
 EBICab 900 technology.} - need citation.
+    \item Minimal grammar corrections and please see the annotated version of the paper.
 \end{itemize}
 
-\section{Minor Remarks}
+\section{Feedback}
+The paper proposes an innovative and practical idea, but is somewhat in further explanation and discussion around the topic.
+There are many topics is worth to be further discussed , that will make the content more informative and meaningful for publishing.
+
+\section{Reviewer Confidence}
+I am not quite familiar with the topic, both telecom and railway system.
+But I can understand most parts of the paper, especially the railway system part, because it provides most comprehensive information.
+
+\section{Evaluation}
+Conditionally accept. But it needs revision with further explanation on the topic.
 

### 2025-03-10 resources/Code/Analyse/Tests/__init__.py

@@ -1,0 +1,4 @@
+# # make it possible to import modules from parent and siblings directory
+# import sys
+# sys.path.append('..')
+

### 2025-03-10 resources/Code/Analyse/__init__.py

@@ -1,0 +1,5 @@
+
+# import sys
+#
+# # make it possible to import modules from parent and siblings directory
+# sys.path.append('..')

### 2025-03-10 resources/Code/Analyse/pcap_analyse.py

@@ -1,0 +1,67 @@
+
+import dpkt
+import io
+import os
+from typing import List, Tuple, Union
+from enum import Enum
+
+class Choice(Enum):
+    TIME_STAMP = 0
+    PAYLOAD = 1
+
+class PcapAnalyse:
+    pcap_file_name: str = None
+    pcap_file_path: os.path = None
+    pcap_file_data = None
+    # MARK: Decoded TCP Payload with Timestamp
+    tcp_payload_with_timestamp: List[Tuple[float, bytearray]] = None
+    start_ts: float = None
+    end_ts: float = None
+    protocol_name: str = None
+
+    def __init__(self, path:os.path, protocol_name:str):
+        self.pcap_file_path = path
+        self.pcap_file_name = os.path.basename(path)
+        pkts = read_pkts(path)
+        self.protocol_name = protocol_name
+        self.pcap_file_data = pkts
+        self.tcp_payload_with_timestamp = retrieve_tcp_payload_with_timestamp(pkts, self.pcap_file_name)
+        self.start_ts = float(pkts[0][0])
+        self.end_ts = float(pkts[-1][0])
+
+
+    def retrieve_tcp_payload_or_timestamp(self, choice: Choice) -> List[
+        Union[float, bytearray]]:
+        if choice == Choice.TIME_STAMP:
+            return [x[Choice.TIME_STAMP.value] for x in self.tcp_payload_with_timestamp]
+        else:
+            return [x[Choice.PAYLOAD.value] for x in self.tcp_payload_with_timestamp]
+
+def read_pkts(pcap_file_path: os.path):
+    with io.open(pcap_file_path, 'rb') as f:
+        pkts = dpkt.pcap.Reader(f).readpkts()
+    return pkts
+
+def retrieve_tcp_payload_with_timestamp(pcapfile, pcap_file_name) -> List[Tuple[float, bytearray]]:
+    l: List[Tuple[float, bytearray]] = []
+    for ts, buff in pcapfile:
+        # Initialize ETH Packet from pcap_buff
+        eth = dpkt.ethernet.Ethernet(buff)
+        # First retrieve IP Packet from Ethernet Packet
+        if len(eth.data) == 0:
+            continue
+        ip = eth.data
+        assert isinstance(ip, dpkt.ip.IP), f'Unknown non IP datatype {eth.data.__class__} in {pcap_file_name}'
+
+        payload_bytes = None
+        # Then retrieve TCP Packet from IP Packet
[…]

### 2025-03-10 resources/Code/Analyse/pcap_fingerprint_analyse.py

@@ -1,0 +1,102 @@
+
+from typing import List
+import dpkt
+
+from pcap_analyse import PcapAnalyse
+
+class PcapFingerprintAnalyse(PcapAnalyse):
+    def __init__(self, pcap_file_name):
+        super().__init__(pcap_file_name)
+
+    @property
+    def cipher_suite(self):
+        return self._handshake_determined_cipher_suite(self.tcp_payload_with_timestamp)
+    # NOTE: We should inspect the cipher suits as it is a significant characteristic of browser or other http client(e.g. curl)
+    @staticmethod
+    def _retrieve_client_cipher_suit_bytes(client_hello):
+        # Since data and header are two component of data, we can use it to retrieve the cipher suit used by the client
+        # The developer had retried the cipher suites, but not store it, so I copy the code here
+        # See https://dpkt.readthedocs.io/en/latest/_modules/dpkt/ssl.html#TLSServerHello.unpack
+        _, pointer = dpkt.ssl.parse_variable_array(client_hello.pack(), 1)
+        cipher_suites, _ = dpkt.ssl.parse_variable_array(client_hello.data[pointer:], 2)
+        return [cipher_suites[i:i + 4] for i in range(0, len(cipher_suites), 4)]
+    @staticmethod
+    def retrieve_client_cipher_suite(client_hello):
+        codes = PcapFingerprintAnalyse._retrieve_client_cipher_suit_bytes(client_hello)
+        cipher_suites = []
+        for code in codes:
+            cipher_suite = dpkt.ssl.ssl_ciphersuites.BY_CODE.get(code, None)
+            if cipher_suite is not None:
+                cipher_suites.append(cipher_suite)
+        return cipher_suites
+
+    @staticmethod
+    def retrieve_server_cipher_suite(server_hello):
+        cipher_suite = dpkt.ssl.ssl_ciphersuites.BY_CODE.get(server_hello.cipher_suite, None)
+        return cipher_suite
+    @staticmethod
+    def retrieve_handshake(tcp_pkt):
+        # Check for SSL packet
+        hs = dpkt.ssl.TLSHandshake(tcp_pkt.data)
+        if not isinstance(hs, dpkt.ssl.TLSHandshake):
+            return None
+        return hs
+
+    """
+        Source code for reference:
+    
+    
+            [docs]
+            class TLSUnknownHandshake(dpkt.Packet):
+                __hdr__ = tuple()
+    
+    
+    
+            TLSServerKeyExchange = TLSUnknownHandshake
[…]

### 2025-03-10 resources/Code/Analyse/pcap_length_analyse.py

@@ -1,0 +1,53 @@
+from array import array
+from math import trunc
+
+from numpy import dtype
+
+from Analyse.pcap_analyse import PcapAnalyse, Choice
+import numpy as np
+# class PcapLengthAnalyse(PcapAnalyse):
+#     def __init__(self, pcap_file_name):
+#         super().__init__(pcap_file_name)
+#
+#     def occurrence_of_length(self):
+#         occurrences = list[int]()
+#         for _, payload in self.tcp_payload_with_timestamp:
+#             occurrences.append(len(payload))
+#         return Counter(occurrences)
+#
+#     def temporal_statistic_of_length(self):
+#         records: list[Tuple[float, int]] = []
+#         for ts, payload in self.tcp_payload_with_timestamp:
+#             records.append((ts, len(payload)))
+#         return records
+
+
+# Generate a histgram of the occurrence of the length of the TCP payload
+# The x-axis is the lengths of the TCP payload (in ranges: bins which has a width of delta)
+# The y-axis is the occurrences of the length
+def occurrence_histogram(analyse: PcapAnalyse, delta: int):
+    occurrences = []
+    for _, payload in analyse.tcp_payload_with_timestamp:
+        l = len(payload)
+        # Filter the zero sized packets
+        if l > 0:
+            occurrences.append(len(payload))
+    assert len(occurrences) > 0, f'Unexpected empty TCP payload in {analyse.pcap_file_name}'
+    max_l = max(occurrences)
+    min_l = min(occurrences)
+    # Prepare np array for plotting
+
+    bins = np.linspace(0, max_l, 60)
+    return occurrences, bins
+
+def temporal_length_array(analysis: PcapAnalyse):
+    t = analysis.retrieve_tcp_payload_or_timestamp(Choice.TIME_STAMP)
+    l = analysis.retrieve_tcp_payload_or_timestamp(Choice.PAYLOAD)
+    p = np.array([int(x - analysis.start_ts) for x in t])
+    q = np.array([int(len(y)) for y in l])
+    # ts = np.asarray(p)
+    # length = np.asarray(q)
+    # max_l = max(len(ts), len(length))
+    # ts.reshape(-1, max_l)
+    # length.reshape(-1, max_l)
+    return p, q

### 2025-03-10 resources/Code/ExtratcTcpFromPcap.sh

@@ -1,0 +1,11 @@
+#!/bin/zsh
+
+# infile = file to input
+# outfile = file to output
+# ext = extension of the output file
+
+for stream in $(tshark -nlr $infile -Y tcp.flags.syn==1 -T fields -e tcp.stream | sort -n | uniq | sed 's/\r//')
+do
+    echo "Processing stream $stream: ${outfile}_${stream}.${ext}"
+    tshark -nlr $infile -qz "follow,tcp,raw,$stream" | tail -n +7 | sed 's/^\s\+//g' | xxd -r -p | tee ${outfile}_${stream}.${ext} >> ${outfile}_all.${ext}
+done

### 2025-03-10 resources/Code/Tests/__init__.py

@@ -1,0 +1,3 @@
+# # make it possible to import modules from parent and siblings directory
+# import sys
+# sys.path.append('.')

### 2025-03-10 resources/Code/Tests/entropy_test.py

@@ -1,0 +1,15 @@
+import unittest
+from Analyse import pcap_entropy_analyse
+from Analyse import pcap_analyse
+import utils
+import io
+
+class TestEntropy(unittest.TestCase):
+    general_entropy_standard_result = 7.977084
+    def test_general_entropy(self):
+        analyse = pcap_analyse.PcapAnalyse(utils.get_pcap_file_path('https'), 'https')
+        result = pcap_entropy_analyse.calculate_general_entropy(analyse)
+        delta = abs(self.general_entropy_standard_result - result)
+        self.assertLessEqual(delta, 0.2, f'[Test failed]: {result} has error {delta} > 0.1')
+if __name__ == '__main__':
+    unittest.main()

### 2025-03-10 resources/Code/Visualisation/entropy_statistics_visualization.py

@@ -1,0 +1,44 @@
+from Analyse.pcap_analyse import PcapAnalyse
+from Analyse.pcap_entropy_analyse import calculate_entropy_per_packet
+import numpy as np
+import matplotlib.pyplot as plt
+import os
+
+def plot_temporal_entropy_statistic_of_protocol_in_temporal_domain(analyse: PcapAnalyse, fig, ax):
+    ts, data = calculate_entropy_per_packet(analyse)
+    ax.plot(ts, data, label=analyse.protocol_name)
+
+def plot_entropy_statistic_in_temporal_domain(save_path:os.path, split=False,**kwargs:PcapAnalyse):
+    fig = plt.figure(figsize=(15, 20))
+    fig.tight_layout()
+    plt.subplots_adjust(hspace=0.2, wspace=0.3)
+    fig.suptitle('Payload Length in Temporal Domain')
+    for index, (protocol_name, analyse) in enumerate(kwargs.items()):
+        # label = analyse.protocol_name
+        ax = fig.add_subplot(2, 3, index + 1)
+        ax.set_xlim(0, 120)
+        ax.set_ylim(0, 8)
+        ax.set_xticks(np.arange(0, 120, 10))
+        ts, data = calculate_entropy_per_packet(analyse)
+        line = ax.plot(ts, data, label=analyse.protocol_name)
+        ax.set_title(f'{protocol_name}')
+        ax.set_xlabel('Time')
+        ax.set_ylabel('Entropy')
+    if not __debug__:
+        plt.savefig(save_path, format='png')
+    plt.show()
+
+def plot_single_temporal_entropy_statistic_of_protocol_in_temporal_domain(save_path:os.path, analyse:PcapAnalyse):
+    fig, ax = plt.subplots()
+    ax.set_xlim(0, 120)
+    ax.set_ylim(0, 8)
+    ax.set_xticks(np.arange(0, 120, 10))
+    ts, data = calculate_entropy_per_packet(analyse)
+    ax.plot(ts, data, label=analyse.protocol_name)
+    ax.set_title(f'{analyse.protocol_name}')
+    ax.set_xlabel('Time (seconds)')
+    ax.set_ylabel('Entropy')
+    if not __debug__:
+        plt.savefig(save_path, format='png')
+    plt.show()
+

### 2025-03-10 resources/Code/Visualisation/length_statistics_visualization.py

@@ -1,0 +1,90 @@
+
+from Analyse.pcap_analyse import PcapAnalyse
+import numpy as np
+import matplotlib.pyplot as plt
+import os
+
+from Analyse.pcap_length_analyse import occurrence_histogram, temporal_length_array
+
+def plot_occurrence_of_length(save_path: PcapAnalyse, **kwargs: os.path):
+    fig = plt.figure(figsize=(15, 20))
+    fig.tight_layout()
+    plt.subplots_adjust(hspace=0.2, wspace=0.3)
+    for index, (protocol_name, analyse) in enumerate(kwargs.items()):
+        ax = fig.add_subplot(2, 3, index + 1)
+        hist, bins = occurrence_histogram(analyse, 5)
+        # ax.set_xlim([0, max(bins)])
+        # ax.set_xticks(np.arange(0, max(bins), 500))
+        ax.hist(hist,
+                bins=bins,
+                color='skyblue',
+                alpha=0.7)
+        ax.set_title(f'{protocol_name}')
+        ax.set_xlabel('Length')
+        ax.set_ylabel('Occurrence')
+    if not __debug__:
+        plt.savefig(save_path, format='png')
+    plt.show()
+
+def plot_single_occurrence_of_length(save_path: os.path, analyse: PcapAnalyse):
+    fig, ax = plt.subplots()
+    hist, bins = occurrence_histogram(analyse, 5)
+    ax.hist(hist,
+            bins=bins,
+            color='skyblue',
+            alpha=0.7)
+    ax.set_title(f'{analyse.protocol_name}')
+    ax.set_xlabel('Length')
+    ax.set_ylabel('Occurrence')
+    if not __debug__:
+        plt.savefig(save_path, format='png')
+    plt.show()
+
+# The temporal statistics of length for every packet for a single protocol
+# We should combine it to a plot in order to compare between different protocols
+def plot_length_statistic_of_protocol_in_temporal_domain(analyse: PcapAnalyse, fig, ax):
+    ts, data = temporal_length_array(analyse)
+    ax.plot(ts, data, label=analyse.protocol_name)
+
+# The combination of all the protocols' graphs
+def plot_length_statistic_in_temporal_domain(save_path: os.path, **kwargs: PcapAnalyse):
+    fig = plt.figure(figsize=(15, 20))
+    fig.tight_layout()
[…]

### 2025-03-10 resources/Code/main.py

@@ -1,0 +1,87 @@
+from Visualisation.entropy_statistics_visualization import plot_entropy_statistic_in_temporal_domain, \
+    plot_single_temporal_entropy_statistic_of_protocol_in_temporal_domain
+from utils import get_pcap_file_path, get_result_file_path
+from Analyse.pcap_analyse import PcapAnalyse
+from Analyse.pcap_entropy_analyse import calculate_entropy_of_data, calculate_general_entropy
+from Visualisation.length_statistics_visualization import plot_occurrence_of_length, \
+    plot_length_statistic_in_temporal_domain, plot_single_occurrence_of_length, \
+    plot_single_length_statistic_in_temporal_domain
+import sys
+protocols = ['naiveproxy', 'trojan', 'shadowsocks', 'obfs4', 'https']
+
+analyses = [PcapAnalyse(get_pcap_file_path(protocol), protocol) for protocol in protocols]
+
+
+
+def main():
+    s = split()
+    entropy_occurrence_statistic_and_analyse(s)
+
+    length_statistic_in_temporal_domain(s)
+
+    entropy_statistic_in_temporal_domain(s)
+
+    get_general_entropy()
+
+def split():
+    s = False
+    if len(sys.argv) > 1:
+        argument = sys.argv[1]
+        s = argument == '--split-output-figure' or argument == '-s'
+    return s
+
+def entropy_occurrence_statistic_and_analyse(split: bool):
+    print('Start [entropy occurrence statistic and analyse]')
+    d = get_kwargs()
+    if split:
+        for protocol_name, analyse in d.items():
+            result_path = get_result_file_path(f'occurrence_of_length_{protocol_name}')
+            plot_single_occurrence_of_length(result_path, analyse)
+            print(f'Plot saved at {result_path}')
+    else:
+        result_path = get_result_file_path('occurrence_of_length')
+        plot_occurrence_of_length(result_path, **d)
+        print(f'Plot saved at {result_path}')
+    print('End [entropy occurrence statistic and analyse]')
+
+def length_statistic_in_temporal_domain(split: bool):
+    print('Start [length statistic in temporal domain]')
+    d = get_kwargs()
+    if split:
+        for protocol_name, analyse in d.items():
+            result_path = get_result_file_path(f'temporal_statistic_of_length_{protocol_name}')
+            plot_single_length_statistic_in_temporal_domain(result_path, analyse)
+            print(f'Plot saved at {result_path}')
+    else:
[…]

### 2025-03-10 resources/Code/utils.py

@@ -1,0 +1,25 @@
+from enum import Enum
+import os
+
+class WorkDirectory(Enum):
+    Data = 0
+    Analyse = 1
+    Visualisation = 2
+    Results = 3
+
+def get_dir_path(dir: WorkDirectory):
+    current_path = os.path.dirname(__file__)
+    dir_path = os.path.join(current_path, dir.name)
+    # if __debug__:
+        # print(f"Directory path: {dir_path}")
+    return dir_path
+
+def get_pcap_file_path(name):
+    pcap_file_name = f'{name}dump.pcap'
+    return os.path.join(get_dir_path(WorkDirectory.Data), 'Pcap', pcap_file_name)
+
+def get_result_file_path(name, extension: str='png'):
+    return os.path.join(get_dir_path(WorkDirectory.Results), f'{name}.{extension}')
+
+# def get_tcp_bin_file_path(name):
+#     return os.path.join(get_dir_path(WorkDirectory.Data), 'Binary',f'{name}tcpdump')

### 2025-03-10 resources/Config/CertsRenewal.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+/home/acme.sh/.acme.sh/acme.sh --register-account -m $MY_EMAIL
+# Issue Certificates
+/home/acme.sh/.acme.sh/acme.sh --server letsencrypt --renew --issue --nginx  -d "<your_domain>" -d "<your_www_domain_with_same_name>" --keylength ec-256
+# Install Certificates for nginx
+/home/acme.sh/.acme.sh/acme.sh --install-cert -d adultlily.com \
+--key-file       /var/www/keys/key.pem  \
+--cert-file      /var/www/certs/cert.pem \
+--fullchain-file /var/www/fullchain-files/fullchain.pem \
+--reloadcmd     "sudo systemctl restart nginx"
